---
title: "additional_analyses"
author: "Emily Chung"
date: "2026-04-21"
output: html_document
---
## Document summary
This document contains additional plots and analyses which are entirely unrelated to the planned analysis of this study.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```


```{r libraries, include=FALSE}
library(here) # setting working directory to the project directory
library(tidyverse)
library(dplyr)

library(ggplot2) # libraries for plotting data
library(gghalves)

library(afex) # libraries for performing planned contrast analyses
library(emmeans)
afex_options(emmeans_model = "multivariate")

```

### Task jumps over time 
Here, I am plotting task jumps overtime. Task jumps is averaged across trials in 8 epochs, each containing 40 trials.

```{r task jumps by epoch, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

training_by_epoch <- read.csv(here("res/training_by_epoch.csv"))

jumps_by_epoch <- ggplot(training_by_epoch, aes(x = epoch, y = group_task_jumps)) +
  geom_point(alpha = 0.7) +
  geom_line() +
  facet_wrap(~ train_type) +
  labs(x = "Epoch", y = "Task Jumps") +
  theme_classic() 

print(jumps_by_epoch)

```


### Transfer Accuracy by First Transfer Condition
To determine whether performance one one transfer condition affected performance on subsequent transfer conditions, I have also plotted accuracy for the first transfer condition people received.

```{r accuracy by first transfer condition, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

all_transfer_data <- read.csv(here("res/all_transfer_data.csv"))

all_transfer_data$first_transfer <- factor(
  all_transfer_data$first_transfer,
  levels = c("novel first", "partial first", "complete first")
)
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
accuracy_by_first_trf <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0.4, 1), breaks = seq(0.4, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_grid(~first_transfer*train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(accuracy_by_first_trf)


```


We can determine whether order affects performance on transfer by assessing for a three way interaction between first transfer condition, group, and transfer condition.

**Interaction is not significant**

```{r order interaction, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
order_anova <- aov_ez('sub',
                      'mean_acc', 
                      all_transfer_data, 
                      between = c("first_transfer", 'train_type'),
                      within = 'transfer')

print(order_anova)

```


### Transfer Accuracy by Task-set

We can also examine whether similarity in the two learned task-sets influences performance on each of the transfer conditions. It may be that when two task sets are more similar (i.e., when there is more overlap in two task-sets), participants are better able to perform partial transfer. The following plot provides an illustration of any differences between the four sets of Task A and B that were given to participants. However, more work would be needed to quantify how similar two task-sets are.

**There is no interaction between task-set configuration, transfer and group.**

```{r transfer by task-set, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
accuracy_by_taskset <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0.4, 1), breaks = seq(0.4, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_grid(~task_set*train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(accuracy_by_taskset)


```


```{r task-set interaction, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
task_set_anova <- aov_ez('sub',
                      'mean_acc', 
                      all_transfer_data, 
                      between = c("task_set", 'train_type'),
                      within = 'transfer')

print(task_set_anova)

```


### Task memory by error type
We can also get the proportion of setting setting errors participants are making for each group. This analysis should be taken with a grain of salf because it the way a setting error and general error is operationalised for the task memory test is complicated.

```{r task memory proportion set errors, echo = FALSE, warning = FALSE}

task_memory_data <- read.csv(here("res/task_memory_summary.csv"))

# pivoting the data into long form
memory_errors <- task_memory_data %>% 
  pivot_longer(cols = c(proportion_setErr1, proportion_setErr2, proportion_genErr1, 
                        proportion_genErr2),
               names_to = 'error_type',
               values_to = 'proportion_errors') %>% 
  select(sub, train_type, mean_locs_correct, error_type, proportion_errors)

error <- rep(c('SetErr', 'SetErr', 'GenErr', 'GenErr'), times = 96)
learned_task <- rep(c("A", "B", "A", "B"), times = 96)

memory_errors$error_type <- as.factor(memory_errors$error_type)
levels(memory_errors$error_type) <- c("GenErrorA", "GenErrorB", "SetErrorA", "SetErrorB")
memory_errors <- cbind(memory_errors, learned_task, error)


```

```{r task memory errors, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

# plotting errors for each sub, and each learned task they made an error on
x_axis_lab <- 'error type'
y_axis_lab <- 'proportion of total errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 

plot_memory_errors <- ggplot(data = memory_errors, 
                mapping = aes(x = error, y = proportion_errors, colour = error, fill = error)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 21, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'grey20', 
               linewidth = 0.5)+
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~ train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(plot_memory_errors)

```

Is there an interaction between error type and train type on task memory?

```{r task memory errors anova, echo=FALSE, warning=FALSE}

# means for each condition
memory_errors_summ <- memory_errors %>% 
  filter(!is.na(proportion_errors)) %>% 
  group_by(train_type, error) %>% 
  summarise(n = n(),
            error_proportion = mean(proportion_errors)) 

# fit the data to an ANOVA model
memory_error_anova <- aov_ez('sub',
                         'proportion_errors', 
                         memory_errors, 
                         between = 'train_type',
                         within = 'error')

print(memory_error_anova)

```
