---
title: "Stable Task Contexts on the Formation of Routines and Learning Transfer"
author: "E. Chung"
output: html_document
date: "2026-01-07"
---
# Document Summary {.tabset .tabset-dropdown}

This document contains the plots and analyses for all measures used to assess performance in the doors experiment. Planned analyses are conducted for the training and transfer phase as outlined in the pregistration document for this study *[INSERT LINK HERE]*.

```{r libraries, include=FALSE}
rm(list = ls())

# load libraries 
library(here) # setting working directory to the project directory
library(tidyverse)
library(dplyr)

library(ggplot2) # libraries for plotting data
library(gghalves)

library(afex) # libraries for performing planned contrast analyses
library(emmeans)
library(BayesFactor)
library(car)
afex_options(emmeans_model = "multivariate")

```


## Training Stage

Three key measures are used to assess performance in the Training Stage:

- **Task jumps**
- **Transition entropy**
- **General Errors**

```{r training dataframes, include=FALSE}

# load dataframes
training_data <- read.csv(here("res/training_jumps_gen-error.csv"))
training_entropy <- read.csv(here("res/training_entropy.csv"))
training_entropy_stay <- read.csv(here("res/training_STAY_entropy.csv"))

```

### Task Jumps

Task Jumps measure the extent to which training causes a mixing of door selections from Task A and B during pursuit of a single target. ‘Task jumps’ record the number of transitions between target locations from task-set A and B per trial. For example, a sequence of four door selections following the pattern of A1-B1-B2-A2 would incur a score of 2. This is due to the switch from task-set A to B on the second door selection, which is followed by a subsequent switch back to Task A on the fourth selection. Transitions to doors which are not relevant to any task are not recorded in this measure, however we do record irrelevant door selections to confirm whether they occur at a rate that is lower than would be expected by chance

```{r task jumps, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

training_data$switch <- factor(
  training_data$switch,
  levels = c("Switch", "Stay")
)

iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_task_jumps
y_axis_lab <- 'Task Jumps'
these_cols <- c("#004aad", "#ffbd59")


task_jumps <- ggplot(data = training_data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.7, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 7.5, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "black", fill = "black") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(colour = NA),
      strip.text = element_text(face = "bold", size = 12),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 12),
      axis.title = element_text(face = 'bold', color = "grey20", size = 14),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(task_jumps)
ggsave(here("res/plots/task_jumps.png"), plot = task_jumps, 
       width = 6, height = 4)

```


#### Planned Analyses

We will perform a 2 (Group: stable vs. variable) x 2 (Trial Type: stay vs. switch) interaction contrast.

Before that, we should check if the data meets the assumptions for homogeneity of variance and normality, by checking if the variance ratio exceed 1.5. The variance ratio is the ratio between the largest and smallest variance values across conditions. We should also check for outliers, which are classified as scored greater than 2.5 SDs from the mean for each grou x trial type condition. The following output shows a summary of the descriptive statistics and number of outliers from each condition.

```{r}

ggplot(training_data, aes(sample = mean_task_jumps)) +
     stat_qq() +
     stat_qq_line(col = "blue") +
     theme_minimal()

training_data <- training_data %>% 
  mutate(log_jumps = log(mean_task_jumps),
         sqrt_jumps = sqrt(mean_task_jumps))

```


```{r task jump descriptives, echo=FALSE, warning=FALSE}
# getting mean, variance and standard deviation for each condition
var_summary <- training_data %>% 
  group_by(train_type, switch) %>% 
  summarise(group_mean_jumps = mean(mean_task_jumps),
            sd = sd(mean_task_jumps),
            var = var(mean_task_jumps))

var_summary <- var_summary %>% 
  mutate(upper_limit = (group_mean_jumps + 2.5*sd),
         lower_limit = (group_mean_jumps - 2.5*sd))

print(var_summary)

# how many participants are considered outliers?
training_with_descriptives <- left_join(training_data, var_summary, by = c("train_type", "switch"))

outliers_summary <- training_with_descriptives %>% 
  filter(mean_task_jumps> upper_limit | mean_task_jumps < lower_limit)
n_outliers_per_cond <- outliers_summary %>% 
  group_by(train_type, switch) %>% 
  summarise(n = n())
print(n_outliers_per_cond)

outlier_ids_jumps <- outliers_summary %>% pull(sub) %>% unique()

```

*The variance ratio for between the largest and smallest variance exceeds 1.5.* Since this is likely driven by a few extreme points which are unlikely to be corrected by transformation, we will perform the analysis as planned with all the data **AND** post-hoc, excluding outliers.

When performed **full data set**, the analysis returns a **significant interaction**, as predicted. The main effect of trial type is also significant.

```{r planned comparisons task jumps, echo=FALSE, warning=FALSE}
# fit the data to an ANOVA model
task_jumps_anova <- aov_ez('sub',
                         'mean_task_jumps', 
                         training_data, 
                         between = 'train_type',
                         within = 'switch')

print(task_jumps_anova)

# get estimated marginal means
task_jumps_emm <- emmeans(task_jumps_anova, c("train_type", "switch"))

print(task_jumps_emm)

```

##### Follow up analyses

To investigate the source of interaction in task jumps, I will contrast task jumps between groups for each trial type separately and across trial types for each group separately.

This analysis returns two significant simple effects. Task jumps is higher on stay trials in the variable group compared to the stable group, and also higher on switch trials than stay trials for the stable group.

```{r task jumps follow up contrasts}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(task_jumps_emm, simple_effects, adjust = "bonferroni")

```

#### Post hoc analyses
Now, we will perform the same analysis **excluding the outliers**. There are 4 data points which are classified as outliers but participants are excluded case wise.

```{r task jumps excluding outliers, echo=FALSE, warning=FALSE}

# remove outliers from training data
training_post_excl <- training_with_descriptives %>% 
  filter(!sub %in% outlier_ids_jumps)

```

```{r task jumps outlier cut offs, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

 # plotting the full training data with dotted lines showing the cutoffs
# data <- training_data
iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_task_jumps
y_axis_lab <- 'Task Jumps'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

task_jumps_cutoffs <- ggplot(data = training_data,
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width",
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3,
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20",
                 outlier.shape = NA) +
    geom_hline(data = training_with_descriptives,
                aes(yintercept = upper_limit), linetype = 'dashed', colour = 'black') +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 7.5, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) +
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10))
    )

print(task_jumps_cutoffs)   
```


This plot shows task jumps after outliers are removed. The scale for this plot is smaller.

```{r task jumps post excl, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}
# now plotting the task jumps data after outliers have been excluded
# data <- training_post_excl
iv <- training_post_excl$switch
x_axis_lab <- 'Trial type'
dv <- training_post_excl$mean_task_jumps
y_axis_lab <- 'Task Jumps'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

task_jumps_postexcl <- 
  ggplot(data = training_post_excl, 
         mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 7.5, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )


print(task_jumps_postexcl)


```


When performed with the data set excluding outliers, *the interaction effect remains significant.* Both main effects of group and trial type also now return significant.

```{r comparisons on task jumps excluding outliers, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
jumps_anova_postexcl <- aov_ez('sub',
                         'mean_task_jumps', 
                         training_post_excl, 
                         between = 'train_type',
                         within = 'switch')

print(jumps_anova_postexcl)

# get estimated marginal means
jumps_emm_postexcl <- emmeans(jumps_anova_postexcl, c("train_type", "switch"))

print(jumps_emm_postexcl)

```

Now for performing the same follow up contrasts. The same contrasts are significant in this analysis, with the *addition of a third significant simple effect* of trial type for the variable group. Task jumps is higher on stay trials than on switch trials for those in the variable group.

```{r task jumps post-excl follow up contrasts, echo=FALSE, warning=FALSE}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(jumps_emm_postexcl, simple_effects, adjust = "bonferroni")

```


### Transition Entropy

Transition entropy quantifies the average variance in participants’ transitions between doors for a given task. First, for each door (or state, [s]) we compute the probability of a transition to the next door (or state, [s’]). We then compute the entropy over the vector of transition probabilities (s -> all s’) and then sum the entropies across all states (Σ(H(s)). This measure quantifies the degree to which a participants’ behaviour during training deviates from being perfectly predictable. Transition entropy during training is averaged across Task A and B. Higher routine variability scores indicate greater variability in search paths during the training stage, and less routine behaviour. 

The following plot and analysis is performed with transition entropy across all trials (switch and stay).
```{r transition entropy, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}
data <- training_entropy
iv <- training_entropy$train_type
x_axis_lab <- 'Group'
dv <- training_entropy$mean_entropy
y_axis_lab <- 'Transition Entropy'
these_cols <- these_cols <- c("#004aad", "#ffbd59")

entropy <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.4,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.4,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.05, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 40, by = 10)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "black", fill = "black") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(colour = NA),
      strip.text = element_text(face = "bold", size = 12),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 12),
      axis.title = element_text(face = 'bold', color = "grey20", size = 14),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(entropy)

ggsave(here("res/plots/entropy.png"), plot = entropy, 
       width = 6, height = 4)

```

```{r TE descriptives, echo=FALSE, warning=FALSE}

var_summary <- training_entropy %>% 
  group_by(train_type) %>% 
  summarise(mean = mean(mean_entropy),
            sd = sd(mean_entropy))

print(var_summary)

```

#### Planned Analyses
A between groups comparison will be performed to determine any differences in transition entropy between groups.

*No difference is detected between groups on transition entropy*

```{r planned comparisons transition entropy, echo=FALSE}
# fit the data to an ANOVA model
entropy_anova <- aov_ez('sub',
                         'mean_entropy', 
                         training_entropy, 
                         between = 'train_type')

print(entropy_anova)

```

#### Exploratory Analyses
A between groups comparison will be performed to determine any differences in transition entropy between groups on **stay** trials only.

*No difference is detected between groups on transition entropy*

```{r transition entropy stay, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}
data <- training_entropy_stay
iv <- training_entropy_stay$train_type
x_axis_lab <- 'Group'
dv <- training_entropy_stay$mean_entropy
y_axis_lab <- 'Transition Entropy on stay trials'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


entropy_stay <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 40, by = 10)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(entropy_stay)

ggsave(here("res/plots/entropy_stay.png"), plot = entropy_stay, 
       width = 7, height = 5)

```

```{r planned comparisons transition entropy on stay trials, echo=FALSE}
# fit the data to an ANOVA model
entropy_stay_anova <- aov_ez('sub',
                         'mean_entropy', 
                         training_entropy_stay, 
                         between = 'train_type')

print(entropy_stay_anova)

```

Why is there a difference in task jumps but no difference between transition entropy between groups? Higher task jumps in the variable group may be due to a greater number of clicks in general. To look at this, we can compare the avaerage number of clicks made by the stable and variable groups across all trials.

```{r nclicks, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

nclicks <- read.csv(here("res/training_nclicks.csv"))
  
data <- nclicks
iv <- nclicks$train_type
x_axis_lab <- 'Group'
dv <- nclicks$nclicks
y_axis_lab <- 'n clicks'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


nclicks_btwn <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(nclicks_btwn)

ggsave(here("res/plots/nclicks.png"), plot = nclicks_btwn, width = 7, height = 5)

```


Is there a subset of people in the stable group who are lost/confused and driving the bimodaility in transition entropy on stay trials? And is this contributing to a higher task jumps and general error scores? We can see if if we plot transition entropy (TE) against task jumps and general errors (see below).

```{r TE subset, echo=FALSE, warning=FALSE}
# first, we should find the subset of participants who fall within the clusters of interest

# getting participants who score > 20 on TE for Stay trials only
TE_subset <- training_entropy_stay %>%  
  filter(mean_entropy > 20)

TE_subset_ids <- TE_subset %>% pull(sub) %>% unique

training_data <- training_data %>%
  mutate(TE_subset = if_else(sub %in% TE_subset_ids,"TRUE", "FALSE"))

# do these participants also have a TE > 20  when calculated over ALL trials? YES
training_subset <- training_entropy %>% 
  filter(sub %in% TE_subset_ids)


```

```{r TE and task jumps, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"} 
# plotting task jumps on stay trials with mean entropy across all trials
training_stay_only <- training_data %>% 
  filter(switch == 'Stay')
training_stay_only <- inner_join(training_stay_only, training_entropy, by = c('sub', 'train_type'))

TE_task_jumps_stay <- ggplot(data = training_stay_only, 
                        mapping = aes(x = mean_entropy, 
                                      y = mean_task_jumps,
                                      color = TE_subset)) +
  geom_point() +
  geom_vline(xintercept = 20, linetype = 'dashed', colour = 'grey') +
  facet_wrap(~train_type) +
  labs(title = 'Jumps on stay trials only',
       x = 'transition entropy (TE)', 
       y = 'task jumps', 
       color = "TE > 20 on stay trials") +
  scale_color_manual(values = c("TRUE" = "#D55E00", "FALSE" = "grey10")) +
  theme_classic()
print(TE_task_jumps_stay)

ggsave(here("res/plots/TExstay-jumps.png"), plot = TE_task_jumps_stay, 
       width = 7, height = 5)

# plotting task jumps on switch trials with mean entropy across all trials
training_switch_only <- training_data %>% 
  filter(switch == 'Switch')
training_switch_only <- inner_join(training_switch_only, training_entropy, by = c('sub', 'train_type'))

TE_task_jumps_switch <- ggplot(data = training_switch_only, 
                        mapping = aes(x = mean_entropy, 
                                      y = mean_task_jumps,
                                      color = TE_subset)) +
  geom_point() +
  geom_vline(xintercept = 20, linetype = 'dashed', colour = 'grey') +
  facet_wrap(~train_type) +
  labs(title = 'Jumps on switch trials only',
       x = 'transition entropy (TE)', 
       y = 'task jumps', 
       color = "TE > 20 on stay trials") +
  scale_color_manual(values = c("TRUE" = "#D55E00", "FALSE" = "grey10")) +
  theme_classic()
print(TE_task_jumps_switch)

ggsave(here("res/plots/TExswitch-jumps.png"), plot = TE_task_jumps_switch, 
       width = 7, height = 5)

```


### General errors

A General Error is made when a door which belongs to neither Task A nor B is selected. General error is used to determine the extent to which memory of target locations is disrupted by the frequency of switching between tasks during training and is represented as a proportion of the total number of door selections made. An average general error of p = 0.4 across trials in the training stage corresponds to chance level performance and thus indicates that a participant has failed to remember the target locations. 

Participants who have an average general error greater than 0.25 on *stay* trials during training will be excluded from analyses of the test phase. No subjects met this criteria, and thus, no participants will be excluded from analyses of transfer phase.

```{r general errors, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

training_data$switch <- factor(
  training_data$switch,
  levels = c("Switch", "Stay")
)

iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_gen_error
y_axis_lab <- 'General Errors'
these_cols <- these_cols <- c("#004aad", "#ffbd59")

gen_errors <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.7, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 1, by = 0.1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "black", fill = "black") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(colour = NA),
      strip.text = element_text(face = "bold", size = 12),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 12),
      axis.title = element_text(face = 'bold', color = "grey20", size = 14),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(gen_errors)   

ggsave(here("res/plots/general_errors.png"), plot = gen_errors, width = 6, height = 4)

```

The following plot shows the distribution of all general error scores, collapsed across group and trial type.

```{r general errors histogram, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

gen_err_hist <- ggplot(data = training_data, aes(x = mean_gen_error)) +
  geom_histogram(fill = 'orange', bins = 30) +
  theme_classic() +
  labs(x = "general error", y = "frequency") +
  scale_y_continuous(breaks = seq(from = 0, to = 70, by = 10)) +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
    )

print(gen_err_hist)
ggsave(here("res/plots/general_error_hist.png"), plot = gen_err_hist, width = 7, height = 5)

```


#### Planned analyses
We will assess for a 2 (Group: stable vs. variable) x 2 (Trial Type: switch vs. stay) interaction for general errors.

First, we will check whether the data violates assumptions of homogeneity of variance and normality for the ANOVA by checking if the variance ratio exceeds 1.5. The following output shows the descriptives data and number of outliers for each Group x Trial Type condition.

```{r general error descriptives, echo = FALSE, warnings = FALSE}
# get mean, variance and standard deviations for each condition
var_summary <- training_data %>% 
  group_by(train_type, switch) %>% 
  summarise(group_mean_error = mean(mean_gen_error),
            sd = sd(mean_gen_error),
            var = var(mean_gen_error))

var_summary <- var_summary %>% 
  mutate(upper_limit = (group_mean_error + 2.5*sd))

print(var_summary)

# how many participants are considered outliers?
training_with_descriptives <- left_join(training_data, var_summary, by = c("train_type", "switch"))

outliers_summary <- training_with_descriptives %>% filter(mean_gen_error > upper_limit)
n_outliers_per_cond <- outliers_summary %>% 
  group_by(train_type, switch) %>% 
  summarise(n = n())
print(n_outliers_per_cond)

outlier_ids_gen_err <- outliers_summary %>% pull(sub) %>% unique()

```

Once again, the variance ratio exceeds 1.5 for general error. As we did with task jumps, we will perform the planned analysis *with the full data set*, AND post-hoc *excluding* outliers.

The following analyses are performed with the **full data set**. The ANOVA performed returns a **significant Group x Trial Type interaction**. A main effect of trial type is detected.

```{r planned comparisons general_errors, echo=FALSE}
# fit the data to an ANOVA model
gen_error_anova <- aov_ez('sub',
                         'mean_gen_error', 
                         training_data, 
                         between = 'train_type',
                         within = 'switch')

print(gen_error_anova)

# get estimated marginal means
gen_error_emm <- emmeans(gen_error_anova, c("train_type", "switch"))

print(gen_error_emm)

```

##### Follow up analyses
Given the significant interaction effect on general errors, I will now contrast general errors between groups for each trial type separately, and between trial types for each group separately.

The effect of trial type is **significant for the stable group**. General errors is higher on switch trials than stay trials.

```{r gen error follow up contrasts}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(gen_error_emm, simple_effects, adjust = "bonferroni")


```

#### Post-hoc Analyses
We will also perform the analysis from above excluding outliers. Outlier cutoffs are marked in a dotted line in the following plot, but participants are excluded casewise.

```{r gen_errors excluding outliers, echo=FALSE, warning=FALSE}

# remove outliers casewise from training data
training_post_excl <- training_with_descriptives %>% 
  filter(!sub %in% outlier_ids_gen_err)

```


```{r general errors with outlier cutoffs, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}
data <- training_data
iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_gen_error
y_axis_lab <- 'General Errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

gen_errors <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    geom_hline(data = var_summary, 
                aes(yintercept = upper_limit), linetype = 'dashed', colour = 'black') +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 1, by = 0.1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(gen_errors)   

```


This plot shows the distribution of the data after excluding outliers.

```{r general errors post exclusion, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}
data <- training_post_excl
iv <- training_post_excl$switch
x_axis_lab <- 'Trial type'
dv <- training_post_excl$mean_gen_error
y_axis_lab <- 'General Errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

gen_errors <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 1, by = 0.1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(gen_errors)   

```

Now, assessing for the same interaction effect with the current data set, we see that the **interaction effect remains**.

```{r comparisons on gen_errors excluding outliers, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
gen_error_anova_post_excl <- aov_ez('sub',
                         'mean_gen_error', 
                         training_post_excl, 
                         between = 'train_type',
                         within = 'switch')

print(gen_error_anova_post_excl)

```

##### Follow Up Analyses
To assess the source of this interaction, we will once again perform the perform the same follow up contrast analyses of simple effects. Analyses with the current data set returns the same significant simple effect of trial type in the stable group.

```{r gen error follow up contrasts post excl}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(gen_error_emm, simple_effects, adjust = "bonferroni")


```


#### Poor performers?
Now, we should check if the same subset of participants who scored > 20 on transition entropy is accounting for the higher general error scores in the stable group. To do this, we can correlate transition entropy with general errors.

```{r TE and general error, echo=FALSE, warning=FALSE, fig.show='hold', out.width='49%'} 
# plotting task jumps on stay trials with mean entropy across all trials

TE_gen_error_stay <- ggplot(data = training_stay_only, 
                        mapping = aes(x = mean_entropy, 
                                      y = mean_gen_error,
                                      color = TE_subset)) +
  geom_point() +
  geom_vline(xintercept = 20, linetype = 'dashed', colour = 'grey') +
  facet_wrap(~train_type) +
  labs(title = 'General Error on stay trials only',
       x = 'transition entropy (TE)', 
       y = 'general error', 
       color = "TE > 20 on stay trials") +
  scale_color_manual(values = c("TRUE" = "#D55E00", "FALSE" = "grey10")) +
  theme_classic()
print(TE_gen_error_stay)

ggsave(here("res/plots/TExstay-gen-error.png"), plot = TE_gen_error_stay, 
       width = 7, height = 5)

# plotting task jumps on switch trials with mean entropy across all trials
TE_gen_error_switch <- ggplot(data = training_switch_only, 
                        mapping = aes(x = mean_entropy, 
                                      y = mean_gen_error,
                                      color = TE_subset)) +
  geom_point() +
  geom_vline(xintercept = 20, linetype = 'dashed', colour = 'grey') +
  facet_wrap(~train_type) +
  labs(title = 'General error on switch trials only',
       x = 'transition entropy (TE)', 
       y = 'general error', 
       color = "TE > 20 on stay trials") +
  scale_color_manual(values = c("TRUE" = "#D55E00", "FALSE" = "grey10")) +
  theme_classic()
print(TE_gen_error_switch)

ggsave(here("res/plots/TExswitch-gen-error.png"), plot = TE_gen_error_switch, 
       width = 7, height = 5)

```

## Training Summary

We were able to replicate findings for task jumps as shown in Barnes et al., (submitted). We found that variable training caused people to preemptively shift between door selections from each house (i.e., mix door selections from the two task sets), while stable training helped keep door selections from task distinct. The mixing of the two task sets in the variable group did not disrupt how routine people were, when searching for targets, because we found no difference in transition entropy between groups, when across task and trial. This is in contrast to previous finding which suggested that variable training significantly interfered with the ability to maintain a consistent routine compared to stable training. The lack of difference between groups for transition entropy may be due to the introduction of a trial-based structure, through the home button added to the display, driving the transition entropy scores down to a level comparable to the stable group. This may suggest that the presence of external factors which signal the start and end of a task are crucial to being able to maintain a routine. This also suggests that what forms part of a task representation is influence by external cues.

In addition, we detected a significant interaction between group and trial type for general errors, which we did not observe in the previous study. This was driven by greater general errors on switch trials compared to stay trials for those in the stable group. 

To investigate the source of this difference we identified 5 participants with an average general error > 0.25 and run all the analyses again (post-hoc) to determine whether these participants was contributing to the interaction effect seen in for general errors in this study. The interaction remained significant after removing these participants. Note: these analyses were run in a separate res_summary_posthoc_excl.Rmd document.


## Transfer Test Stage

Three key measures are used to assess performance during the Transfer Test Stage of the experiment.

- **Accuracy**
- **Learning Onset**
- **Setting Error**

```{r transfer dataframes, include=FALSE}

# load dataframes
all_transfer_data <- read.csv(here("res/all_transfer_data.csv"))
learn_onset_data <- read.csv(here("res/post_exclusion_transfer_data.csv"))
non_learners <- read.csv(here("res/nonlearners.csv"))

all_btwn_transfer_data <- read.csv(here("res/all_btwn_transfer_data.csv"))
btwn_non_learners <- read.csv(here("res/btwn_nonlearners.csv"))
learn_onset_btwn_data <- read.csv(here("res/post_exclusion_btwn_data.csv"))

task_memory_data <- read.csv(here("res/task_memory_summary.csv"))
ind_diffs <- read.csv(here("res/all_individual_differences.csv"))

```

### Accuracy

Accuracy is a measure of performance in the transfer task. It is the proportion of door selections which are relevant to the current task, relative to the total number of door selections. Accuracy is averaged across trials for each participant. 

```{r accuracy, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

# specifying the order that I want my transfer conditions to appear
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Partial", "Complete", "Novel")
)

# specifying key variables
data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#00bf63", "#ff66c4", "#ff914d")

# plotting now
jitter_pos <- position_dodge(width = 0.2) 
  
accuracy <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 1.5, 
               colour = "grey20", fill = "grey20") +
  stat_summary(aes(group = iv),
               fun.data = mean_se, 
               geom = "errorbar", 
               width = 0.05,  
               colour = "grey20") +
  scale_y_continuous(limits = c(0.4, 1), breaks = seq(0.4, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(colour = "NA"),
    strip.text = element_text(face = "bold", size = 12),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 12),
    axis.title = element_text(face = "bold", color = "grey20", size = 14),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(accuracy) 

ggsave(here("res/plots/accuracy_full.png"), plot = accuracy, 
       width = 6, height = 4)

```

### Descriptives for accuracy
```{r acc descriptives, echo=FALSE, warning=FALSE}

var_summary <- all_transfer_data %>% 
  group_by(train_type, transfer) %>% 
  summarise(mean = mean(mean_acc),
            sd = sd(mean_acc))

print(var_summary)

transfer_cond_desc <-  all_transfer_data %>% 
  group_by(transfer) %>% 
  summarise(mean = mean(mean_acc),
            sd = sd(mean_acc))

```


#### Planned Analyses
Planned bonferroni contrasts are performed for the following comparisons.

- main effect of training - 1. stable v.s. variable training
- main effects of transfer - 1. novel v.s. partial, 2. novel v.s. complete, 3. partial v.s. complete
- interaction effects - 1. group x transfer (novel vs. partial) and 2. group x transfer (partial vs. complete)

*Only the main effect of novel vs. complete transfer returned significant. Difference between novel and part almost returns significant*

```{r planned comparisons accuracy, echo=FALSE}
# fit the data to an ANOVA model
accuracy_anova <- aov_ez('sub',
                         'mean_acc', 
                         all_transfer_data, 
                         between = 'train_type',
                         within = 'transfer')

print(accuracy_anova)

# get estimated marginal means
accuracy_emm <- emmeans(accuracy_anova, c("train_type", "transfer"))

print(accuracy_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_acc <- contrast(accuracy_emm, within_main, adjust = "bonferroni")

print(transfer_main_acc)


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_acc <- contrast(accuracy_emm, interactions, adjust = "bonferroni")

print(interactions_acc)

```

To remove mitigate any order effects, accuracy can be assessed using a between subjects design, by comparing performance on the first transfer condition across groups. This however, significantly reduces power.

```{r accuracy between subjects, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

# specifying the order that I want my transfer conditions to appear
# all_btwn_transfer_data$transfer <- factor(
#   all_transfer_data$transfer,
#   levels = c("Novel", "Partial", "Complete")
# )

# specifying key variables
data <- all_btwn_transfer_data
iv <- all_btwn_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_btwn_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

# now plotting
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
acc_between_subs <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0.5, 1), breaks = seq(0.5, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(acc_between_subs) 

```


In a separate analyses, we will regress order onto accuracy, and perform the group comparisons on the residuals. **This analysis returns the same results as above**.

```{r regressing order onto accuracy, echo=FALSE, warning=FALSE}

# regress order onto acc and get residuals
acc_regress_order <- lm(mean_acc ~ order_id, data = all_transfer_data)
summary(acc_regress_order)
acc_residuals <- resid(acc_regress_order)

# add residuals to subject data 
acc_residuals <- cbind(all_transfer_data, acc_residuals) %>% 
  select(sub, train_type, transfer, order_id, first_transfer, acc_residuals)

```

```{r planned comparisons accuracy residuals, echo=FALSE}
# fit the data to an ANOVA model
acc_resid_anova <- aov_ez('sub',
                         'acc_residuals', 
                         acc_residuals, 
                         between = 'train_type',
                         within = 'transfer')

print(acc_resid_anova) # significant main effect of transfer

# get estimated marginal means
acc_resid_emm <- emmeans(acc_resid_anova, c("train_type", "transfer"))

print(acc_resid_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_acc <- contrast(acc_resid_emm, within_main, adjust = "bonferroni")

print(transfer_main_acc) # novel versus comp comparison significant


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_acc <- contrast(acc_resid_emm, interactions, adjust = "bonferroni")

print(interactions_acc) # no significant interactions

```

#### Regressing bias scores onto transition entropy
To determine whether the strength of a routine correlated with performance in transfer, we will also correlate transition entropy to bias scores for partial transfer accuracy, relative to performance on the:
1. novel condition where bias = partial/(partial + novel)
2. complete transfer where bias = partial/(partial + complete)

To do this, we will first check whether the data for transition entropy and the bias scores is skewed.

```{r bias and TE skewness, echo = FALSE, warning = FALSE, fig.show='hold', out.width="49%"}

bias_scores <- read.csv(here("res/transfer_bias_scores.csv"))

# histograms
ggplot(data = bias_scores, aes(x = bias_ovr_complete)) +
  geom_histogram(fill = 'pink') +
  theme_classic() +
  labs(x = "Bias Score: Partial/(Partial + Complete)", y = "Frequency") +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))

ggplot(data = bias_scores, aes(x = bias_ovr_novel)) +
  geom_histogram(fill = 'pink') +
  theme_classic() +
  labs(x = "Bias Score: Partial/(Partial + Novel)", y = "Frequency") +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))

ggplot(data = training_entropy, aes(x = mean_entropy)) +
  geom_histogram(fill = 'pink') +
  theme_classic() +
  labs(x = "Transition entropy", y = "Frequency") +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))

# Q-Q plots
qq_novel_bias <- ggplot(data = bias_scores, aes(sample = bias_ovr_novel)) + 
  geom_qq(colour = 'blue') +
  geom_qq_line(color = "grey")+
  labs(title = "Q-Q plot for bias scores partial/(partial + novel)",
        x = 'theoretical',
        y = 'sample') +
  # labs(title = 'Q-Q plots for transition entropy',
  #      x = 'theoretical',
  #      y = 'sample') +
  theme_classic() +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))


ggsave(here("res/plots/qq_novel_bias.png"), plot = qq_novel_bias, width = 7, height = 5)

```

Based off visual inspection of Q-Q plots, the data for transition entropy and bias are skewed. Hence, a log transformation will be performed on the data.

```{r transforming bias scores and TE, echo = FALSE, warnings = FALSE}

# combined the data into one data frame first
bias_scores <- inner_join(bias_scores, training_entropy, by = c('sub', 'train_type'))

bias_scores <- bias_scores %>% 
  mutate(log_bias_comp = log(bias_ovr_complete),
         log_bias_novel = log(bias_ovr_novel),
         log_entropy= log(mean_entropy))

```

Now, lets visualise the transformed data in Q-Q plots again.

```{r Q-Q plots post transformation, echo = FALSE, warnings = FALSE, fig.show='hold', out.width="49%"}

# Q-Q plots
qq_TE_transformed <- ggplot(data = bias_scores, aes(sample = log_entropy)) + 
  geom_qq(colour = 'blue') +
  geom_qq_line(color = "grey")+
  # labs(title = "Q-Q plot for bias scores partial/(partial + complete) post transformation",
  #       x = 'theoretical',
  #       y = 'sample') +
   labs(title = 'Q-Q plots for transition entropy post transformation',
        x = 'theoretical',
        y = 'sample') +
  theme_classic() +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))

ggsave(here("res/plots/qq_TE_transformed.png"), plot = qq_TE_transformed, width = 7, height = 5)


```

Now we can plot the correlation between transition entropy and the two bias scores.
```{r TE and bias correlation, echo = FALSE, warning = FALSE}

# correlating TE with bias scores over complete accuracy
TExcomplete_bias <- ggplot(data = bias_scores,
                           aes(x = mean_entropy,
                               y = bias_ovr_complete)) +
  geom_point(colour = "orange") +
  theme_classic()
print(cor(bias_scores$bias_ovr_complete, bias_scores$mean_entropy)) # r = 0.01
model <- lm(bias_scores$bias_ovr_complete ~ bias_scores$mean_entropy)
summary(model)

# correlating TE with bias scores over novel accuracy
TExnovel_bias <- ggplot(data = bias_scores,
                           aes(x = mean_entropy,
                               y = bias_over_novel)) +
  geom_point(colour = "orange") +
  theme_classic()
print(cor(bias_scores$bias_ovr_novel, bias_scores$mean_entropy)) # r = 0.12

print(TExcomplete_bias)

```


### Learning Onset
Learning onset quantifies how long it takes to learn the target locations by determining the trial at which there is evidence for knowledge of all four target locations in each task.  

Learning onset is calculated using a Bayesian algorithm (Maggi et al., 2024) which applies the beta distribution to model the amount of evidence for a particular behavioural strategy on a trial-by-trial basis. To do this, every trial is assessed for whether it contains evidence for an informed (non-guessed) selection of each door. 

Criteria for coding evidence of doors for learning onset are as follows:
* all door selections made before an error scored a 1
* all door selections made after an error are scored a 0
* any missing door selections are scored a 1, if there was evidence of knowledge for that door on the most recent trial it was selected. If else, assign it a value of NA.

E.g., for a door sequence of door selections ‘A-B-X-Y-C', doors A and B are assigned a value of 1, door C is assigned 0. Door D which is missing from the sequence of clicks is assigned 1, if it was correctly selected before an error on the last trial a click on Door D was recorded, and NA if else. 

```{r learning onset, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

# specifying the order that I want my transfer conditions to appear
learn_onset_data$transfer <- factor(
  learn_onset_data$transfer,
  levels = c("Partial", "Complete", "Novel")
)

# specifying key variables
data <- learn_onset_data
iv <- learn_onset_data$transfer
x_axis_lab <- 'Transfer type'
dv <- learn_onset_data$k4_onset
y_axis_lab <- 'Learning Onset'
these_cols <- c("#00bf63", "#ff66c4", "#ff914d")

# now plot
jitter_pos <- position_dodge(width = 0.2) 
  
learning_onset <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub),
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  # geom_boxplot(width = 0.2, 
  #              alpha = 0.8, 
  #              linewidth = 0.3, 
  #              colour = 'grey20', 
  #             outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(aes(group = iv),
               fun.data = mean_se, 
               geom = "errorbar", 
               width = 0.05,  
               colour = "grey20") +
  scale_y_continuous(limits = c(0, 40), breaks = seq(0, 40, by = 10)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(colour = "NA"),
    strip.text = element_text(face = "bold", size = 12),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 12),
    axis.title = element_text(face = "bold", color = "grey20", size = 14),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(learning_onset)

ggsave(here("res/plots/learn_onset.png"), plot = learning_onset, 
       width = 6, height = 4)

```

Note: 12 cases who never meet the criteria for learning onset are not included in the figure above. The number of subjects in each group who are considered 'non-learners' are outlined below.

```{r non-learners, echo=FALSE, warning=FALSE}

print(non_learners)

```

Again, we can look at the learning onset data in a between subjects manner.

```{r between learning onset, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}
data <- learn_onset_btwn_data
iv <- learn_onset_btwn_data$transfer
x_axis_lab <- 'Transfer type'
dv <- learn_onset_btwn_data$k4_onset
y_axis_lab <- 'Learning Onset'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")


jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
between_learning_onset <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 40), breaks = seq(0, 40, by = 10)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(between_learning_onset)

```

Note: 5 participants never met the criteria for having learned all 4 doors and are not included in the previous figure. Performance for these participants are as follows.

```{r between non learners, echo=FALSE, warning=FALSE}

print(btwn_non_learners)

```

```{r acc descriptives, echo=FALSE, warning=FALSE}

var_summary <- learn_onset_data %>% 
  group_by(train_type, transfer) %>% 
  summarise(mean = mean(k4_onset),
            sd = sd(k4_onset))

print(var_summary)

transfer_cond_desc <-  learn_onset_data %>% 
  group_by(transfer) %>% 
  summarise(mean = mean(k4_onset),
            sd = sd(k4_onset))

```

#### Planned Analyses
Planned contrasts are performed for learning onset as they are for accuracy. *No comparisons return significant.*

```{r planned comparisons learn onset, echo=FALSE, warnings = FALSE}
# fit the data to an ANOVA model
learn_onset_anova <- aov_ez('sub',
                         'k4_onset', 
                         learn_onset_data, 
                         between = 'train_type',
                         within = 'transfer')

print(learn_onset_anova)

# get estimated marginal means
learn_onset_emm <- emmeans(learn_onset_anova, c("train_type", "transfer"))

print(learn_onset_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_learn_onset<- contrast(learn_onset_emm, within_main, adjust = "bonferroni")

print(transfer_main_learn_onset)


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_learn_onset <- contrast(learn_onset_emm, interactions, adjust = "bonferroni")

print(interactions_learn_onset)

```



Now, we will regress the order conditions onto learning onset and perform the same planned analyses.
**Results from these analysis are the same as above**

```{r regressing order onto learn onset, echo=FALSE, warning=FALSE}

# regress order onto acc and get residuals
onset_regress_order <- lm(k4_onset ~ order_id, data = learn_onset_data)
summary(onset_regress_order)
onset_residuals <- resid(onset_regress_order)

# add residuals to subject data 
onset_residuals <- cbind(learn_onset_data, onset_residuals) %>% 
  select(sub, train_type, transfer, order_id, first_transfer, onset_residuals)

```

```{r planned comparisons learn onset residuals, echo=FALSE}
# fit the data to an ANOVA model
onset_resid_anova <- aov_ez('sub',
                         'onset_residuals', 
                         onset_residuals, 
                         between = 'train_type',
                         within = 'transfer')

print(onset_resid_anova) # no significant effects

# get estimated marginal means
onset_resid_emm <- emmeans(onset_resid_anova, c("train_type", "transfer"))

print(onset_resid_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_acc <- contrast(onset_resid_emm, within_main, adjust = "bonferroni")

print(transfer_main_acc) # no significant effects


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_acc <- contrast(onset_resid_emm, interactions, adjust = "bonferroni")

print(interactions_acc) # no significant interactions

```

### Number of locations learned

This measure tells us whether participants are following a strategy of using 1, 2, 3, or 4 target locations on the last trial of each transfer condition (i.e., by the end of that transfer condition).

```{r ndoors learned, echo = FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

# specifying the order that I want my transfer conditions to appear
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

# specifying key variables
data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$n_learned
y_axis_lab <- 'N locations learned'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

# now plot
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
ndoors <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub),
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0,4), breaks = seq(0, 4, by = 1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(ndoors)

```

#### Planned Analyses
Planned contrasts are performed for n learned as they are for accuracy and learn onset. *No comparisons return significant.*

```{r planned comparisons n learned, echo=FALSE, warnings = FALSE}
# fit the data to an ANOVA model
ndoors_anova <- aov_ez('sub',
                         'n_learned', 
                         all_transfer_data, 
                         between = 'train_type',
                         within = 'transfer')

print(ndoors_anova)

# get estimated marginal means
ndoors_emm <- emmeans(ndoors_anova, c("train_type", "transfer"))

print(ndoors_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_ndoors<- contrast(ndoors_emm, within_main, adjust = "bonferroni")

print(transfer_main_ndoors)


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_ndoors <- contrast(ndoors_emm, interactions, adjust = "bonferroni")

print(interactions_ndoors)

```

### Setting Errors
Setting-error quantifies the extent to which participants apply previously learned target locations which are not relevant to the current task. Since the number of relevant doors differ between the transfer and novel conditions, setting-error for partial and complete transfer will be calculated differently to the novel task condition.  

For partial and complete transfer, setting-error is calculated as the proportion of total door selections which were previously relevant to Task A or B but have not been transferred to the current task-setting. 

For the novel task condition, setting-error will be calculated as the proportion of door selections from Task A and B. 

```{r setting errors, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

# specifying the order I want transfer conditions to appear in
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_set_error
y_axis_lab <- 'Setting Error'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
setting_error <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 0.5), breaks = seq(0, 0.4, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(setting_error)

ggsave(here("res/plots/setting_error.png"), plot = setting_error, width = 7, height = 5)

```


#### Planned Analyses
We will perform a 2 (Group: stable vs variable) x 2 Transfer(partial vs. complete) contrast analysis, and a separate between groups comparison of setting error on the novel transfer condition.

*No significant differences from any of these contrasts.*

```{r planned analyses setting error, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
set_error_anova <- aov_ez('sub',
                         'mean_set_error', 
                         all_transfer_data, 
                         between = 'train_type',
                         within = 'transfer')

print(set_error_anova)

# get estimated marginal means
set_error_emm <- emmeans(set_error_anova, c("train_type", "transfer"))

print(set_error_emm)

# specify contrasts and run analyses for:
# interaction family (k = 1)
interaction <- c(0, 0, 1, -1, -1, 1)
interactions <- list("groupxpartialvs.complete" = interaction)
interaction_set_error <- contrast(set_error_emm, interactions, adjust = "bonferroni")

print(interaction_set_error)

## simple effects, (k = 1)
group_effect_novel <- c(1, -1, 0, 0, 0, 0)
group_simple_effects <- list(group_effect_novel)
group_effect_set_error <- contrast(set_error_emm, group_simple_effects, adjust = "bonferroni")

print(group_effect_set_error)


```

Again, we can look at Setting Errors using as between subjects design again.

```{r setting error between subjects, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}
data <- all_btwn_transfer_data
iv <- all_btwn_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_btwn_transfer_data$mean_set_error
y_axis_lab <- 'Setting Error'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
set_error_between_subs <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 0.5), breaks = seq(0, 0.5, by = 0.1))  +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(set_error_between_subs) # same order issue as above

```

## Transfer Summary
We did not find any effect of training in stable task contexts on transfer performance. This suggests that the introduction of a trial based search may have mitigated (/prevented) against decrements (/benefits) to partial transfer seen in the stable (/variable) when a continuous search was used, by enforcing a clear start and end point, rather than the amount of task mixing(/interference) experienced during training. The extent that stable contexts and task mixing (/interference) influences transfer may play a role when there is not a clear start an end point to a routine. This contradicts previous findings that being less routine allows people to adapt to novel tasks better.

Does this also suggest that having a routine with a fixed start and end point allows us to **better compartmentalise component behaviour** and perform to transfer in a flexible manner by virture of being able to track component steps better? I.e., have we made the variable more routine, but also better at dissociating between component bethaviours better?  

Is it both? **1 - being able to compartmentalise tasks into components**, but  **2 - not chain these into a single string of events i.e., create associations within the components of the task**. How can we look at this?

In addition, participants once again performed at ceiling, which suggests that our transfer conditions were not sufficiently difficult to tease apart performance on each condition this may have also contributed to the lack of an ability to observe differences in performance. Future work could consider increasing the difficulty of the transfer tasks to better draw out differences between the types of transfer. For example, we could increase the number of target locations from 4 to 6. 


## Task Memory

```{r target memory dataframes, include=FALSE}

# load dataframes
task_memory_data <- read.csv(here("res/task_memory_summary.csv"))

```

### Target location memory
```{r task location memory, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}
data <- task_memory_data
iv <- task_memory_data$train_type
x_axis_lab <- 'Group'
dv <- task_memory_data$mean_locs_correct
y_axis_lab <- 'mean locations correct'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


task_mem <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    # scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 4, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(task_mem)


```

We can compare the number of target locations remembered between groups to determine whether training or transfer interrupted memory of the locations.

```{r ttest task location memory, echo = FALSE, warning = FALSE}

ttestBF(formula = mean_locs_correct ~ train_type, data = ind_diffs)

```


#### Task memory by transfer
Now, we can also compare the look at whether the proportion of doors remembered each learned task, in terms of whether it was transferred to the complete condition, partial condition, both, or not transferred at all.

```{r task memory wrt. transfer tasks, echo = FALSE, warning = FALSE}

# pivoting the data into long form
task_memory_by_trf <- task_memory_data %>% 
  pivot_longer(cols = c(comp_and_part, complete_only, partial_only, never_transferred),
               names_to = 'transferred_to',
               values_to = 'proportion_correct') %>% 
  select(sub, train_type, mean_locs_correct, all_complete, transferred_to, proportion_correct)

```

```{r plot task memory wrt. transfer tasks, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

task_memory_by_trf$transferred_to <- factor(task_memory_by_trf$transferred_to,  # keeps the order of the conditions
                                            levels = unique(task_memory_by_trf$transferred_to))

# renaming conditions
levels(task_memory_by_trf$transferred_to) <- c("Both", "Complete Only", "Partial Only", "Never transferred")

# now plot
x_axis_lab <- 'Learned Locations by Transfer Condition'
y_axis_lab <- 'Proportion Correct'
these_cols <- c("#004aad", "#00bf63", "#ff66c4", "#ff914d")


plot_memory_by_trf <- ggplot(data = task_memory_by_trf, 
                mapping = aes(x = transferred_to, y = proportion_correct, colour = transferred_to, fill = transferred_to)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = position_dodge(width = 0.3)) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 1.5, 
               colour = "black", fill = "black") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'black', 
               linewidth = 0.4)+
  scale_y_continuous(breaks = seq(0, 1, by = 0.5)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~ train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(colour = "NA"),
    strip.text = element_text(margin = margin(b = 10),
                              face = "bold", 
                              size = 11),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 10),
    axis.title = element_text(face = "bold", color = "grey20", size = 13),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(plot_memory_by_trf)

ggsave(here("res/plots/task_memory_by_trf.png"), plot = plot_memory_by_trf, width = 6, height = 4)

```


```{r memory by groupxtransferred doors, echo-FALSE, warning=FALSE}

memory_means <- task_memory_by_trf %>% 
  group_by(train_type, transferred_to) %>% 
  summarise(mean(proportion_correct))
print(memory_means)

memory_by_trf_anova <- aov_ez('sub',
                         'proportion_correct', 
                         task_memory_by_trf, 
                         between = 'train_type',
                         within = 'transferred_to')

print(memory_by_trf_anova)

```

We can also split this comparison by whether people received complete before partial, or complete after partial, and when complete transfer came up in the transfer stage.

```{r getting transfer order by complete before or after partial, echo=FALSE, warning=FALSE}

# first, we should get the order that participants performed complete transfer, relative to partial
# and the position of complete transfer
order_data <- all_transfer_data %>% 
  select(sub, train_type, order_id) %>% 
  mutate(comp_vs_part_order = case_when(order_id %in% c(2, 3, 4) ~ "Complete before Partial",
                                        order_id %in% c(1, 5, 6)    ~ "Complete after Partial"),
         complete_pos = case_when(order_id %in% c(3, 4) ~ "1st",
                                  order_id %in% c(2, 5) ~ "2nd",
                                  order_id %in% c(1, 6) ~ "3rd")) %>% 
  unique()

task_memory_by_trf <- inner_join(task_memory_by_trf, order_data, by = c('sub', 'train_type'))

```

```{r plot task memory by complete position relative to partial, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

# reordering variables
task_memory_by_trf$comp_vs_part_order <- factor(task_memory_by_trf$comp_vs_part_order,
                                                levels = c("Complete before Partial", "Complete after Partial"))

# now plot
x_axis_lab <- 'Learned Locations by Transfer Condition'
y_axis_lab <- 'Proportion Correct'
these_cols <- c("#004aad", "#00bf63", "#ff66c4", "#ff914d")

plot_transfer_order <- ggplot(data = task_memory_by_trf, 
                mapping = aes(x = transferred_to, y = proportion_correct, colour = transferred_to, fill = transferred_to)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = position_dodge(width = 0.3)) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 1.5, 
               colour = "black", fill = "black") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'black', 
               linewidth = 0.3)+
  scale_y_continuous(breaks = seq(0, 1, by = 0.5)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~ comp_vs_part_order) +
  theme(
    legend.position = "none",
    strip.background = element_rect(colour = "NA"),
    strip.text = element_text(margin = margin(b = 10),
                              face = "bold", 
                              size = 11),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 10),
    axis.title = element_text(face = "bold", color = "grey20", size = 13),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(plot_transfer_order)

ggsave(here("res/plots/task_memory_by_trf_order.png"), plot = plot_transfer_order, width = 6, height = 4)

```

```{r memory by order x transfer, echo=FALSE, warning=FALSE}

memory_means <- task_memory_by_trf %>% 
  group_by(comp_vs_part_order, transferred_to) %>% 
  summarise(mean(proportion_correct))
print(memory_means)

memory_orderxtrf_anova <- aov_ez('sub',
                         'proportion_correct', 
                         task_memory_by_trf, 
                         between = 'comp_vs_part_order',
                         within = 'transferred_to')

print(memory_orderxtrf_anova)

```

#### Is there a recency effect of complete training on memory of the complete task set?
There are some participants who fail to remember the locations of the task transferred to the complete condition. We want to know whether this is due to a recency effect of performing complete transfer 1st, 2nd or 3rd during the transfer test phase. If there is a recency effect, we should see poorer memory of the complete task in participants who performed complete transfer first and the best memory in those who performed complete transfer 3rd.

```{r getting complete memory data, echo=FALSE, warning=FALSE}

complete_memory <- task_memory_by_trf %>% 
  select(-transferred_to, -proportion_correct) %>% 
  group_by(sub, train_type, all_complete, order_id, comp_vs_part_order, complete_pos) %>% 
  unique()

```

```{r complete recency effect, echo=FALSE, warning=FALSE, fig.show='hold', out.width="49%"}

complete_memory$complete_pos <- factor(complete_memory$complete_pos,  # keeps the order of the conditions
                                            levels = c('1st', '2nd', '3rd'))

# now plot
x_axis_lab <- 'complete transfer position'
y_axis_lab <- 'n correct'
these_cols <- c("#004aad", "#00bf63", "#ff66c4")
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 

complete_recency <- ggplot(data = complete_memory, 
                mapping = aes(x = complete_pos, y = all_complete, colour = complete_pos, fill = complete_pos)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 21, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'grey20', 
               linewidth = 0.5)+
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~ train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(complete_recency)

ggsave(here("res/plots/task_memory_recency.png"), plot = complete_recency, width = 7, height = 5)

```

```{r complete recency anova, echo=FALSE, warning=FALSE}

memory_means <- complete_memory %>% 
  group_by(train_type, complete_pos) %>% 
  summarise(mean(all_complete))
print(memory_means)

complete_recency_anova <- aov_ez('sub',
                         'all_complete', 
                         complete_memory, 
                         between = c('complete_pos', 'train_type'))

print(complete_recency_anova)

```


## Task Memory Summary
We compared memory for the two learned task sets and found no differences between groups. This suggests that the training manipulation did not affect participants memory of the two task sets. Memory was also not affected by the order of conditions during the transfer test stage. That is performing complete transfer before partial transfer did not affect memory of doors to a different extent than if complete was performed after partial transfer. There was also no recency effect of performing complete 1st, 2nd or 3rd in memory of the relevant target locations.

Does this suggest that both groups were equally able to distinguish the two task sets? i.e., did we sucessfully manipulate task representations using training?


## Individual differences

To determine whether its worthwhile performing the individual difference data analyses, we can look at the variance in the data for those measures.

```{r individual diff dataframes, include=FALSE}

# load dataframes
ind_diffs <- read.csv(here("res/all_individual_differences.csv"))

```

### Spatial WM (corsi)

Here, I am visualising the spread of the data for the forward and backward version of the corsi task.

```{r spatial WM, echo=FALSE, fig.show='hold', out.width="49%"}

x <- ind_diffs$max_fwd_corsi[is.finite(ind_diffs$max_fwd_corsi)]
y <- ind_diffs$max_bwd_corsi[is.finite(ind_diffs$max_bwd_corsi)]

hist(x,
     main = "forward spatial WM",
     xlab = "maximum recalled",
     col = "lightblue")
hist(y,
     main = "backwards spatial WM",
     xlab = "maximum recalled",
     col = "lightblue")

spatialWM_desc <- ind_diffs %>% 
  summarise(fwd_mean = mean(x),
            bwd_mean = mean(y),
            fwd_var = var(x),
            bwd_var = var(y))

```

### Verbal WM (digit span)

Here, I am visualising the spread of the digit span data.

```{r verbal WM, echo=FALSE, fig.show='hold', out.width="49%"}

x <- ind_diffs$max_fw_digits
y <- ind_diffs$max_bw_digits

hist(x,
     main = "forward verbal WM",
     xlab = "digit span",
     col = "lightblue")

hist(y,
     main = "backwards spatial WM",
     xlab = "digit span",
     col = "lightblue")

plot(x, y,
     xlab = "forward digit span",
     ylab = "backwards digit span",
     pch = 19,        
     col = "blue")

verbalWM_desc <- ind_diffs %>% 
  summarise(fwd_mean = mean(max_fw_digits),
            bwd_mean = mean(max_bw_digits),
            fwd_var = var(max_fw_digits),
            bwd_var = var(max_bw_digits))

```

### Does working memory predict the formation of routines? Regressing WM measures on TE, Task jumps, and rule learning ratings

To determine whether spatial working memory may underly how routine people are, we can regress the spatial and verbal working memory measures onto transition entropy, task jumps and rule learning rating from the acqusition stage in separate multiple regression analyses.

```{r checking for normality, echo=FALSE, warnings=FALSE}

# loading average jumps and rule learning data
average_jumps <- read.csv(here("res/training_average_jumps.csv"))
jumps_transforms <- average_jumps %>%  # transforming task jumps data
  mutate(sqrt_jumps = sqrt(jumps),
         log_jumps = log(jumps + 0.01)) # use log transform when looking at task jumps

rule_learning_transforms <- ind_diffs %>%  # transformations are not helpful. will use scores as is.
  mutate(sqrt_rule_acq = sqrt(acq_rule_score),
         log_rule_acq = log(acq_rule_score))

# run this code to get qq plot
ggplot(jumps_transforms, aes(sample = log_jumps)) + # change data frame and variable as required
  stat_qq() +
  stat_qq_line() +
  theme_minimal()

```

```{r getting regression data, echo=FALSE, warning=FALSE}

# adding transition entropy and jumps data to ind_diffs file to run regression
regression_data <- inner_join(ind_diffs, jumps_transforms, by = c('sub', 'train_type'))
regression_data <- inner_join(regression_data, training_entropy, by = c('sub', 'train_type'))

# removing participants with missing spatial working memory data
regression_data <- regression_data %>% 
  filter(is.finite(max_fwd_corsi) & is.finite(max_bwd_corsi)) %>% 
  select(-task_config, -ncorrectA, -ncorrectB, -mean_locs_correct, -acq_open_resp, 
         -train_rule_score, -train_open_resp)

write.csv(regression_data, file = "res/regression_data.csv", row.names = FALSE)

```

Let's also see the correlation between the variable in this data set.
```{r ind diffs cor, echo=FALSE, warning=FALSE}

vars <- regression_data %>% 
  select(-sub, -train_type, - sqrt_jumps, -log_jumps)

corr_mat <- cor(vars)
print(corr_mat)

```


Now, we will perform **three separate regressions**.

1. Transition Entropy

The model for this regression is significant, but follow up tests of individual predictors using the Benjamin-Hochberg procedure revealed no significant results. Data checked for multicollinearity, using variance inflation factors (VIF) and tolerance values which are all at an acceptable level. 

```{r regressing ind diffs on TE, echo=FALSE, warning=FALSE, fig.show='hold', out.width="24.9%"}

# TE as criterion
TE <- lm(mean_entropy ~ max_fwd_corsi + max_bwd_corsi + max_fw_digits + max_bw_digits,
         data=regression_data)
summary(TE) # model is significant
vif <- vif(TE)
tolerance <- 1/vif # tolerance is all > 0.1 

TE_coefs <- coef(TE)

plot(TE)

```

```{r TE FDR, echo=FALSE, warnings=FALSE}

raw_p <- c(0.0583, 0.06, 0.4990, 0.1691) 

fdr_p <- p.adjust(raw_p, method = "fdr") 
print(fdr_p) # no predictors are significant, all p's > 0.05

```

2. Task Jumps

The model for this regression is significant. Follow up tests of individual predictors using the Benjamin Hochberg procedure revealed no significant predictors. Data checked for multicollinearity, using variance inflation factors (VIF) and tolerance values which are at an acceptable level.

```{r regress ind diffs on TE, echo=FALSE, warning=FALSE, fig.show='hold', out.width="24.9%"}

# Task jumps as criterion
jumps <- lm(log_jumps ~ max_fwd_corsi + max_bwd_corsi + max_fw_digits + max_bw_digits, 
            data = regression_data)
summary(jumps) # model is significant
vif <- vif(jumps)
tolerance <- 1/vif # tolerance is all > 0.1 

plot(jumps)

```

```{r jumps FDR, echo=FALSE, warnings=FALSE}

raw_p <- c(0.1195, 0.0187, 0.3171, 0.0281) 

fdr_p <- p.adjust(raw_p, method = "fdr") 
print(fdr_p) # none are significant with log transformation, all p's > 0.05

```


3. Rule learning ratings (task acquisition stage)

This model did not produce a significant result. No follow up tests of individual predictors were performed.

```{r regressing ind diffs on rule learning scores, echo=FALSE, warning=FALSE, fig.show='hold', out.width="24.9%"}

# rule learning ratings
acq_rule_score <- lm(acq_rule_score ~ max_fwd_corsi + max_bwd_corsi + max_fw_digits + max_bw_digits,
                     data = regression_data)
summary(acq_rule_score) # model is not significant

vif <- vif(acq_rule_score)
tolerance <- 1/vif

plot(acq_rule_score)

```

I will also perform run these three regression analysis in **a multivariate multiple regression** with a follow up MANOVA test to better understand how each predictor contributed to common variance between TE and task jumps. None of the predictors come out significant in the MANOVA model.

```{r multivariate multiple regression, echo=FALSE, warning=FALSE}

# multivariate multiple regression
mlm1 <- lm(cbind(mean_entropy, jumps) ~ max_fwd_corsi +
             max_bwd_corsi + max_fw_digits + max_bw_digits, 
           data = regression_data)
summary(mlm1)

Anova(mlm1) # all predictors are insignificant, all p's >0.05 

```

```{r MANOVA FDR adjustment, echo=FALSE, warnings=FALSE}

raw_p <- c(0.1326, 0.0857, 0.1654, 0.0376) 

fdr_p <- p.adjust(raw_p, method = "fdr") 
print(fdr_p) # none are significant, all p's > 0.05

```


Now, let run the same analyses with Group (train_type) added as a predictor.

1. Transition Entropy with Group

The model for this regression is **still** significant and in line with the previous analysis, follow up tests of individual predictors using the Benjamin-Hochberg procedure revealed no significant results. 

```{r regressing ind diffs on TE w/ group, echo=FALSE, warning=FALSE, fig.show='hold', out.width="24.9%"}

# TE as criterion
TE <- lm(mean_entropy ~  train_type + max_fwd_corsi + max_bwd_corsi + max_fw_digits + max_bw_digits,
         data=regression_data)
summary(TE) # model is significant
vif <- vif(TE)
tolerance <- 1/vif # tolerance is all > 0.1 

plot(TE)

```


```{r TE FDR w/ group, echo=FALSE, warnings=FALSE}

raw_p <- c(0.768609, 0.063980, 0.067783, 0.493239, 0.165831)

fdr_p <- p.adjust(raw_p, method = "fdr") # all p > 0.05
print(fdr_p) # no predictors are significant, all p's > 0.05

``` 

2. Task jumps with Group

The model for this regression is **still** significant. Follow up tests of individual predictors using the Benjamin Hochberg procedure revealed backward digit span, **and group** to be significant predictors of performance of task jumps. 

```{r regressing ind diffs on TExgroup, echo=FALSE, warning=FALSE, fig.show='hold', out.width="24.9%"}

# Task jumps as criterion
jumps <- lm(log_jumps ~ train_type + max_fwd_corsi + max_bwd_corsi + max_fw_digits + max_bw_digits, 
            data = regression_data)
summary(jumps) # model is significant
vif <- vif(jumps)
tolerance <- 1/vif # tolerance is all > 0.1 

plot(jumps)

```

```{r jumps FDR w/group, echo=FALSE, warning=FALSE}

raw_p <- c(0.000183, 0.176494, 0.036139, 0.209077, 0.008194) 

fdr_p <- p.adjust(raw_p, method = "fdr") 
print(fdr_p) # train_type and max_bw_digits are significant

```


3. Rule learning scale with Group (task acquisition stage)

This model is not significant.

```{r regressing ind diffs on rule learning scores w/ group, echo=FALSE, warning=FALSE, fig.show='hold', out.width="24.9%"}

# rule learning ratings
acq_rule_score <- lm(acq_rule_score ~ train_type + max_fwd_corsi + max_bwd_corsi + max_fw_digits +
                       max_bw_digits,
                    data = regression_data)
summary(acq_rule_score) # model is not significant

vif <- vif(acq_rule_score)
tolerance <- 1/vif

plot(acq_rule_score)

```

And now, using **a multivariate multiple regression analysis** which includes group. Group and backwards digit span are significant predictors of common variance between TE and jumps. Interestingly, it is verbal working memory that contributes to TE and jumps, rather than spatial working memory.

```{r multivariate multiple regression with group, echo=FALSE, warning=FALSE}

# multivariate multiple regression
mlm2 <- lm(cbind(mean_entropy, log_jumps) ~ train_type + max_fwd_corsi +
             max_bwd_corsi + max_fw_digits + max_bw_digits, 
           data = regression_data)
summary(mlm2)

Anova(mlm2) # train type and backwards digit span are significant

```

```{r MANOVA with group FDR adjustment, echo=FALSE, warning=FALSE}

raw_p <- c(0.0000001431, 0.17619, 0.11019, 0.39149, 0.01395) 

fdr_p <- p.adjust(raw_p, method = "fdr") 
print(fdr_p) # train type and bwd_digits span is significant.

```


### Does working memory performance predict performance on Transfer?

Given that working memory affects performance on transition entropy and task jumps, we can also examine whether working memory also affects transfer. To do this, I will regress Group and all spatial and verbal working memory measures onto accuracy and learn onset using a multivariate multiple regression.

1. Accuracy
This model is not significant.

```{r accuracy wide form, echo=FALSE, warning=FALSE}

acc_wide <- all_transfer_data %>% 
  select(sub, train_type, transfer, mean_acc) %>% 
  pivot_wider(names_from = transfer, values_from = mean_acc)

acc_regression_data <- inner_join(regression_data, acc_wide, by = c('sub', 'train_type'))

```

Without Group:
```{r regressing ind diffs on accuracy, echo=FALSE, warning=FALSE}

# performing multivariate multiple regression for transfer accuracy
mlm1 <- lm(cbind(Novel, Partial, Complete) ~ max_fwd_corsi +
             max_bwd_corsi + max_fw_digits + max_bw_digits, 
           data = acc_regression_data)
summary(mlm1) # this model is not significant

```


With Group:

```{r regressing ind diffs on accuracy with group, echo=FALSE, warning=FALSE}

# performing multivariate multiple regression for transfer accuracy
mlm1 <- lm(cbind(Novel, Partial, Complete) ~ train_type + max_fwd_corsi +
             max_bwd_corsi + max_fw_digits + max_bw_digits, 
           data = acc_regression_data)
summary(mlm1) # this model is not significant

```


2. Learning onset
This model is not significant.

```{r learn onsest wide form, echo=FALSE, warning=FALSE}

onset_wide <- learn_onset_data %>% 
  select(sub, train_type, transfer, k4_onset) %>% 
  pivot_wider(names_from = transfer, values_from = k4_onset)

onset_regression_data <- inner_join(regression_data, onset_wide, by = c('sub', 'train_type'))

```

Without Group:

```{r regressing ind diffs on learn onset, echo=FALSE, warning=FALSE}

# performing multivariate multiple regression for transfer accuracy
mlm1 <- lm(cbind(Novel, Partial, Complete) ~max_fwd_corsi +
             max_bwd_corsi + max_fw_digits + max_bw_digits, 
           data = onset_regression_data)
summary(mlm1) # this model is also not significant

```

With Group:

```{r regressing ind diffs on learn onset with group, echo=FALSE, warning=FALSE}

# performing multivariate multiple regression for transfer accuracy
mlm1 <- lm(cbind(Novel, Partial, Complete) ~ train_type + max_fwd_corsi +
             max_bwd_corsi + max_fw_digits + max_bw_digits, 
           data = onset_regression_data)
summary(mlm1) # this model is also not significant

```

In summary, the working memory measures and type of training **did not** affect transfer accuracy or learning onset.


### Is there an interaction between group, working memory and routiness on learning transfer? Multivariate analysis of individual differences, training contexts and transition entropy on learning transfer

As per the preregistration, we can determine whether there is a relationship between working memory, the stability of training contexts and routines on learning transfer. To do this I will perform a multivariate multiple regression of all rule learning ratings, spatial working memory scores, transition entropy, and group on bias scores for accuracy and learning onset.

```{r transfer data wrangling, echo=FALSE, warning=FALSE}

regression_data <- inner_join(ind_diffs, training_entropy, by = c('sub', 'train_type')) %>% 
  select(-acq_open_resp, -train_open_resp)
regression_data <- inner_join(regression_data, bias_scores, by = c('sub', 'train_type')) %>% 
  select(-ses, -task_set, -task_config, - mean_locs_correct) %>% 
  filter(is.finite(max_fwd_corsi) & is.finite(max_bwd_corsi))

```

```{r transfer MANOVA, echo=FALSE, warning=FALSE}

mlm1 <- lm(cbind(bias_ovr_novel, bias_ovr_complete) ~ train_type + max_fwd_corsi +
             max_bwd_corsi + max_fw_digits + max_bw_digits + acq_rule_score + mean_entropy,
           data = regression_data)
summary(mlm1)

Anova(mlm1)

```


