---
title: "doors results summary"
author: "E. Chung"
output: html_document
date: "2026-01-07"
---
# Document Summary

This document contains the plots and analyses for all measures used to assess performance in the doors experiment. Planned analyses are conducted for the training and transfer phase as outlined in the pregistration document for this study *[INSERT LINK HERE]*.

```{r setup, include=FALSE}
# load libraries 
library(here) # setting working directory to the project directory
library(tidyverse)
library(dplyr)

library(ggplot2) # libraries for plotting data
library(wesanderson)
library(gghalves)

library(afex) # libraries for performing planned contrast analyses
library(emmeans)
library(BayesFactor)
afex_options(emmeans_model = "multivariate")

# load dataframes
training_data <- read.csv(here("res/training_jumps_gen-error.csv"))
training_entropy <- read.csv(here("res/training_entropy.csv"))
training_entropy_stay <- read.csv(here("res/training_STAY_entropy.csv"))
training_by_epoch <- read.csv(here("res/training_by_epoch.csv"))

all_transfer_data <- read.csv(here("res/all_transfer_data.csv"))
non_learners <- read.csv(here("res/nonlearners.csv"))
learn_onset_data <- read.csv(here("res/post_exclusion_transfer_data.csv"))

all_btwn_transfer_data <- read.csv(here("res/all_btwn_transfer_data.csv"))
btwn_non_learners <- read.csv(here("res/btwn_nonlearners.csv"))
learn_onset_btwn_data <- read.csv(here("res/post_exclusion_btwn_data.csv"))


ind_diffs <- read.csv(here("res/all_individual_differences.csv"))

```

## Training Stage

Three key measures are used to assess performance in the Training Stage:
- Task jumps 
- Transition entropy
- General Errors

### Task Jumps

Task Jumps measure the extent to which training causes a mixing of door selections from Task A and B during pursuit of a single target. ‘Task jumps’ record the number of transitions between target locations from task-set A and B per trial. For example, a sequence of four door selections following the pattern of A1-B1-B2-A2 would incur a score of 2. This is due to the switch from task-set A to B on the second door selection, which is followed by a subsequent switch back to Task A on the fourth selection. Transitions to doors which are not relevant to any task are not recorded in this measure, however we do record irrelevant door selections to confirm whether they occur at a rate that is lower than would be expected by chance

```{r task jumps, echo=FALSE, warning=FALSE}
data <- training_data
iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_task_jumps
y_axis_lab <- 'Task Jumps'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


task_jumps <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 7.5, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(task_jumps)

ggsave(here("res/plots/task_jumps.png"), plot = task_jumps, 
       width = 7, height = 5)

```

#### Planned Analyses

We will perform a 2 (Group: stable vs. variable) x 2 (Trial Type: stay vs. switch) interaction contrast.

Before that, we should check if the data meets the assumptions for homogeneity of variance and normality, by checking if the variance ratio exceed 1.5. The variance ratio is the ratio between the largest and smallest variance values across conditions. We should also check for outliers, which are classified as scored greater than 2.5 SDs from the mean for each grou x trial type condition. The following output shows a summary of the descriptive statistics and number of outliers from each condition.

```{r variance on task jump conditions, echo=FALSE, warning=FALSE, fig.show="hold"}
# getting mean, variance and standard deviation for each condition
var_summary <- training_data %>% 
  group_by(train_type, switch) %>% 
  summarise(group_mean_jumps = mean(mean_task_jumps),
            sd = sd(mean_task_jumps),
            var = var(mean_task_jumps))

var_summary <- var_summary %>% 
  mutate(upper_limit = (group_mean_jumps + 2.5*sd),
         lower_limit = (group_mean_jumps - 2.5*sd))

print(var_summary)

# how many participants are considered outliers?
training_with_descriptives <- left_join(training_data, var_summary, by = c("train_type", "switch"))

outliers_summary <- training_with_descriptives %>% 
  filter(mean_task_jumps> upper_limit | mean_task_jumps < lower_limit)
n_outliers_per_cond <- outliers_summary %>% 
  group_by(train_type, switch) %>% 
  summarise(n = n())
print(n_outliers_per_cond)

outlier_ids_jumps <- outliers_summary %>% pull(sub) %>% unique()

```

*The variance ratio for between the largest and smallest variance exceeds 1.5.* Since this is likely driven by a few extreme points which are unlikely to be corrected by transformation, we will perform the analysis as planned with all the data **AND** post-hoc, excluding outliers.

When performed **full data set**, the analysis returns a **significant interaction**, as predicted. The main effect of trial type is also significant.

```{r planned comparisons task jumps, echo=FALSE, warning=FALSE}
# fit the data to an ANOVA model
task_jumps_anova <- aov_ez('sub',
                         'mean_task_jumps', 
                         training_data, 
                         between = 'train_type',
                         within = 'switch')

print(task_jumps_anova)

# get estimated marginal means
task_jumps_emm <- emmeans(task_jumps_anova, c("train_type", "switch"))

print(task_jumps_emm)

```

##### Follow up analyses

To investigate the source of interaction in task jumps, I will contrast task jumps between groups for each trial type separately and across trial types for each group separately.

This analysis returns two significant simple effects. Task jumps is higher on stay trials in the variable group compared to the stable group, and also higher on switch trials than stay trials for the stable group.

```{r task jumps follow up contrasts}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(task_jumps_emm, simple_effects, adjust = "bonferroni")

```

#### Post hoc analyses
Now, we will perform the same analysis **excluding the outliers**. There are 4 data points which are classified as outliers but participants are excluded case wise.

```{r task jumps excluding outliers, echo=FALSE, warning=FALSE}

# remove outliers from training data
training_post_excl <- training_with_descriptives %>% 
  filter(!sub %in% outlier_ids_jumps)

```

```{r task jumps outlier cut offs, echo=FALSE, warning=FALSE, fig.show='hold', out.width="50%"}

 # plotting the full training data with dotted lines showing the cutoffs
# data <- training_data
iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_task_jumps
y_axis_lab <- 'Task Jumps'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

task_jumps_cutoffs <- ggplot(data = training_data,
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width",
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3,
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20",
                 outlier.shape = NA) +
    geom_hline(data = training_with_descriptives,
                aes(yintercept = upper_limit), linetype = 'dashed', colour = 'black') +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 7.5, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) +
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10))
    )

print(task_jumps_cutoffs)   
```


This plot shows task jumps after outliers are removed. The scale for this plot is smaller.

```{r task jumps post excl, echo=FALSE, warning=FALSE}
# now plotting the task jumps data after outliers have been excluded
# data <- training_post_excl
iv <- training_post_excl$switch
x_axis_lab <- 'Trial type'
dv <- training_post_excl$mean_task_jumps
y_axis_lab <- 'Task Jumps'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

task_jumps_postexcl <- 
  ggplot(data = training_post_excl, 
         mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 7.5, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )


print(task_jumps_postexcl)


```


When performed with the data set excluding outliers, *the interaction effect remains significant.* Both main effects of group and trial type also now return significant.

```{r comparisons on task jumps excluding outliers, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
jumps_anova_postexcl <- aov_ez('sub',
                         'mean_task_jumps', 
                         training_post_excl, 
                         between = 'train_type',
                         within = 'switch')

print(jumps_anova_postexcl)

# get estimated marginal means
jumps_emm_postexcl <- emmeans(jumps_anova_postexcl, c("train_type", "switch"))

print(jumps_emm_postexcl)

```

Now for performing the same follow up contrasts. The same contrasts are significant in this analysis, with the *addition of a third significant simple effect* of trial type for the variable group. Task jumps is higher on stay trials than on switch trials for those in the variable group.

```{r task jumps post-excl follow up contrasts, echo=FALSE, warning=FALSE}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(jumps_emm_postexcl, simple_effects, adjust = "bonferroni")

```


### Transition Entropy

Transition entropy quantifies the average variance in participants’ transitions between doors for a given task. First, for each door (or state, [s]) we compute the probability of a transition to the next door (or state, [s’]). We then compute the entropy over the vector of transition probabilities (s -> all s’) and then sum the entropies across all states (Σ(H(s)). This measure quantifies the degree to which a participants’ behaviour during training deviates from being perfectly predictable. Transition entropy during training is averaged across Task A and B. Higher routine variability scores indicate greater variability in search paths during the training stage, and less routine behaviour. 

The following plot and analysis is performed with transition entropy across all trials (switch and stay).
```{r transition entropy, echo = FALSE, warning=FALSE}
data <- training_entropy
iv <- training_entropy$train_type
x_axis_lab <- 'Group'
dv <- training_entropy$mean_entropy
y_axis_lab <- 'Transition Entropy'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

entropy <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 40, by = 10)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(entropy)

ggsave(here("res/plots/entropy.png"), plot = entropy, 
       width = 7, height = 5)

```

#### Planned Analyses
A between groups comparison will be performed to determine any differences in transition entropy between groups.

*No difference is detected between groups on transition entropy*

```{r planned comparisons transition entropy, echo=FALSE}
# fit the data to an ANOVA model
entropy_anova <- aov_ez('sub',
                         'mean_entropy', 
                         training_entropy, 
                         between = 'train_type')

print(entropy_anova)

```

#### Exploratory Analyses
A between groups comparison will be performed to determine any differences in transition entropy between groups on **stay** trials only.

*No difference is detected between groups on transition entropy*

```{r transition entropy stay, echo = FALSE, warning=FALSE}
data <- training_entropy_stay
iv <- training_entropy_stay$train_type
x_axis_lab <- 'Group'
dv <- training_entropy_stay$mean_entropy
y_axis_lab <- 'Transition Entropy on stay trials'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


entropy_stay <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 40, by = 10)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(entropy_stay)

ggsave(here("res/plots/entropy_stay.png"), plot = entropy_stay, 
       width = 7, height = 5)

```

```{r planned comparisons transition entropy on stay trials, echo=FALSE}
# fit the data to an ANOVA model
entropy_stay_anova <- aov_ez('sub',
                         'mean_entropy', 
                         training_entropy_stay, 
                         between = 'train_type')

print(entropy_stay_anova)

```

Why is there a difference in task jumps but no difference between transition entropy between groups? Higher task jumps in the variable group may be due to a greater number of clicks in general. To look at this, we can compare the avaerage number of clicks made by the stable and variable groups across all trials.

```{r nclicks, echo=FALSE, warning=FALSE}

nclicks <- read.csv(here("res/training_nclicks.csv"))
  
data <- nclicks
iv <- nclicks$train_type
x_axis_lab <- 'Group'
dv <- nclicks$nclicks
y_axis_lab <- 'n clicks'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


nclicks_btwn <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(nclicks_btwn)

ggsave(here("res/plots/nclicks.png"), plot = nclicks_btwn, width = 7, height = 5)

```


Is there a subset of people in the stable group who are lost/confused and driving the bimodaility in transition entropy on stay trials? And is this contributing to a higher task jumps and general error scores? We can see if if we plot transition entropy (TE) against task jumps and general errors (see below).

```{r TE subset, echo-FALSE, warning=FALSE}
# first, we should find the subset of participants who fall within the clusters of interest

# getting participants who score > 20 on TE for Stay trials only
TE_subset <- training_entropy_stay %>%  
  filter(mean_entropy > 20)

TE_subset_ids <- TE_subset %>% pull(sub) %>% unique

training_data <- training_data %>%
  mutate(TE_subset = if_else(sub %in% TE_subset_ids,"TRUE", "FALSE"))

# do these participants also have a TE > 20  when calculated over ALL trials? YES
training_subset <- training_entropy %>% 
  filter(sub %in% TE_subset_ids)


```

```{r TE and task jumps, echo=FALSE, warning=FALSE} 
# plotting task jumps on stay trials with mean entropy across all trials
training_stay_only <- training_data %>% 
  filter(switch == 'Stay')
training_stay_only <- inner_join(training_stay_only, training_entropy, by = c('sub', 'train_type'))

TE_task_jumps_stay <- ggplot(data = training_stay_only, 
                        mapping = aes(x = mean_entropy, 
                                      y = mean_task_jumps,
                                      color = TE_subset)) +
  geom_point() +
  geom_vline(xintercept = 20, linetype = 'dashed', colour = 'grey') +
  facet_wrap(~train_type) +
  labs(title = 'Jumps on stay trials only',
       x = 'transition entropy (TE)', 
       y = 'task jumps', 
       color = "TE > 20 on stay trials") +
  scale_color_manual(values = c("TRUE" = "#D55E00", "FALSE" = "grey10")) +
  theme_classic()
print(TE_task_jumps_stay)

ggsave(here("res/plots/TExstay-jumps.png"), plot = TE_task_jumps_stay, 
       width = 7, height = 5)

# plotting task jumps on switch trials with mean entropy across all trials
training_switch_only <- training_data %>% 
  filter(switch == 'Switch')
training_switch_only <- inner_join(training_switch_only, training_entropy, by = c('sub', 'train_type'))

TE_task_jumps_switch <- ggplot(data = training_switch_only, 
                        mapping = aes(x = mean_entropy, 
                                      y = mean_task_jumps,
                                      color = TE_subset)) +
  geom_point() +
  geom_vline(xintercept = 20, linetype = 'dashed', colour = 'grey') +
  facet_wrap(~train_type) +
  labs(title = 'Jumps on switch trials only',
       x = 'transition entropy (TE)', 
       y = 'task jumps', 
       color = "TE > 20 on stay trials") +
  scale_color_manual(values = c("TRUE" = "#D55E00", "FALSE" = "grey10")) +
  theme_classic()
print(TE_task_jumps_switch)

ggsave(here("res/plots/TExswitch-jumps.png"), plot = TE_task_jumps_switch, 
       width = 7, height = 5)

```


### General errors

A General Error is made when a door which belongs to neither Task A nor B is selected. General error is used to determine the extent to which memory of target locations is disrupted by the frequency of switching between tasks during training and is represented as a proportion of the total number of door selections made. An average general error of p = 0.4 across trials in the training stage corresponds to chance level performance and thus indicates that a participant has failed to remember the target locations. 

Participants who have an average general error greater than 0.25 on *stay* trials during training will be excluded from analyses of the test phase. No subjects met this criteria, and thus, no participants will be excluded from analyses of transfer phase.

```{r general errors, echo = FALSE, warning=FALSE}
data <- training_data
iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_gen_error
y_axis_lab <- 'General Errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

gen_errors <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 1, by = 0.1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(gen_errors)   

ggsave(here("res/plots/general_errors.png"), plot = gen_errors, width = 7, height = 5)

```

The following plot shows the distribution of all general error scores, collapsed across group and trial type.

```{r general errors histogram, echo = FALSE, warning=FALSE}

gen_err_hist <- ggplot(data = training_data, aes(x = mean_gen_error)) +
  geom_histogram(fill = 'orange', bins = 30) +
  theme_classic() +
  labs(x = "general error", y = "frequency") +
  scale_y_continuous(breaks = seq(from = 0, to = 70, by = 10)) +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
    )

print(gen_err_hist)
ggsave(here("res/plots/general_error_hist.png"), plot = gen_err_hist, width = 7, height = 5)

```


#### Planned analyses
We will assess for a 2 (Group: stable vs. variable) x 2 (Trial Type: switch vs. stay) interaction for general errors.

First, we will check whether the data violates assumptions of homogeneity of variance and normality for the ANOVA by checking if the variance ratio exceeds 1.5. The following output shows the descriptives data and number of outliers for each Group x Trial Type condition.

```{r variance on general error conditions, echo = FALSE, warnings = FALSE}
# get mean, variance and standard deviations for each condition
var_summary <- training_data %>% 
  group_by(train_type, switch) %>% 
  summarise(group_mean_error = mean(mean_gen_error),
            sd = sd(mean_gen_error),
            var = var(mean_gen_error))

var_summary <- var_summary %>% 
  mutate(upper_limit = (group_mean_error + 2.5*sd))

print(var_summary)

# how many participants are considered outliers?
training_with_descriptives <- left_join(training_data, var_summary, by = c("train_type", "switch"))

outliers_summary <- training_with_descriptives %>% filter(mean_gen_error > upper_limit)
n_outliers_per_cond <- outliers_summary %>% 
  group_by(train_type, switch) %>% 
  summarise(n = n())
print(n_outliers_per_cond)

outlier_ids_gen_err <- outliers_summary %>% pull(sub) %>% unique()

```

Once again, the variance ratio exceeds 1.5 for general error. As we did with task jumps, we will perform the planned analysis *with the full data set*, AND post-hoc *excluding* outliers.

The following analyses are performed with the **full data set**. The ANOVA performed returns a **significant Group x Trial Type interaction**. A main effect of trial type is detected.

```{r planned comparisons general_errors, echo=FALSE}
# fit the data to an ANOVA model
gen_error_anova <- aov_ez('sub',
                         'mean_gen_error', 
                         training_data, 
                         between = 'train_type',
                         within = 'switch')

print(gen_error_anova)

# get estimated marginal means
gen_error_emm <- emmeans(gen_error_anova, c("train_type", "switch"))

print(gen_error_emm)

```

##### Follow up analyses
Given the significant interaction effect on general errors, I will now contrast general errors between groups for each trial type separately, and between trial types for each group separately.

The effect of trial type is **significant for the stable group**. General errors is higher on switch trials than stay trials.

```{r gen error follow up contrasts}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(gen_error_emm, simple_effects, adjust = "bonferroni")


```

#### Post-hoc Analyses
We will also perform the analysis from above excluding outliers. Outlier cutoffs are marked in a dotted line in the following plot, but participants are excluded casewise.

```{r gen_errors excluding outliers, echo=FALSE, warning=FALSE}

# remove outliers casewise from training data
training_post_excl <- training_with_descriptives %>% 
  filter(!sub %in% outlier_ids_gen_err)

```


```{r general errors with outlier cutoffs, echo = FALSE, warning=FALSE}
data <- training_data
iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_gen_error
y_axis_lab <- 'General Errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

gen_errors <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    geom_hline(data = var_summary, 
                aes(yintercept = upper_limit), linetype = 'dashed', colour = 'black') +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 1, by = 0.1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(gen_errors)   

```


This plot shows the distribution of the data after excluding outliers.

```{r general errors post exclusion, echo = FALSE, warning=FALSE}
data <- training_post_excl
iv <- training_post_excl$switch
x_axis_lab <- 'Trial type'
dv <- training_post_excl$mean_gen_error
y_axis_lab <- 'General Errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

gen_errors <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 1, by = 0.1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(gen_errors)   

```

Now, assessing for the same interaction effect with the current data set, we see that the **interaction effect remains**.

```{r comparisons on gen_errors excluding outliers, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
gen_error_anova_post_excl <- aov_ez('sub',
                         'mean_gen_error', 
                         training_post_excl, 
                         between = 'train_type',
                         within = 'switch')

print(gen_error_anova_post_excl)

```

##### Follow Up Analyses
To assess the source of this interaction, we will once again perform the perform the same follow up contrast analyses of simple effects. Analyses with the current data set returns the same significant simple effect of trial type in the stable group.

```{r gen error follow up contrasts post excl}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(gen_error_emm, simple_effects, adjust = "bonferroni")


```


#### Poor performers?
Now, we should check if the same subset of participants who scored > 20 on transition entropy is accounting for the higher general error scores in the stable group. To do this, we can correlate transition entropy with general errors.

```{r TE and general error, echo=FALSE, warning=FALSE} 
# plotting task jumps on stay trials with mean entropy across all trials

TE_gen_error_stay <- ggplot(data = training_stay_only, 
                        mapping = aes(x = mean_entropy, 
                                      y = mean_gen_error,
                                      color = TE_subset)) +
  geom_point() +
  geom_vline(xintercept = 20, linetype = 'dashed', colour = 'grey') +
  facet_wrap(~train_type) +
  labs(title = 'General Error on stay trials only',
       x = 'transition entropy (TE)', 
       y = 'general error', 
       color = "TE > 20 on stay trials") +
  scale_color_manual(values = c("TRUE" = "#D55E00", "FALSE" = "grey10")) +
  theme_classic()
print(TE_gen_error_stay)

ggsave(here("res/plots/TExstay-gen-error.png"), plot = TE_gen_error_stay, 
       width = 7, height = 5)

# plotting task jumps on switch trials with mean entropy across all trials
TE_gen_error_switch <- ggplot(data = training_switch_only, 
                        mapping = aes(x = mean_entropy, 
                                      y = mean_gen_error,
                                      color = TE_subset)) +
  geom_point() +
  geom_vline(xintercept = 20, linetype = 'dashed', colour = 'grey') +
  facet_wrap(~train_type) +
  labs(title = 'General error on switch trials only',
       x = 'transition entropy (TE)', 
       y = 'general error', 
       color = "TE > 20 on stay trials") +
  scale_color_manual(values = c("TRUE" = "#D55E00", "FALSE" = "grey10")) +
  theme_classic()
print(TE_gen_error_switch)

ggsave(here("res/plots/TExswitch-gen-error.png"), plot = TE_gen_error_switch, 
       width = 7, height = 5)

```


## Transfer Test Stage

Three key measures are used to assess performance during the Transfer Test Stage of the experiment.
* Accuracy
* Learning Onset
* Setting Error


### Accuracy

Accuracy is a measure of performance in the transfer task. It is the proportion of door selections which are relevant to the current task, relative to the total number of door selections. Accuracy is averaged across trials for each participant. 

```{r accuracy, echo = FALSE, warning=FALSE}

# specifying the order that I want my transfer conditions to appear
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

# specifying key variables
data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

# plotting now
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
accuracy <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0.4, 1), breaks = seq(0.4, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(accuracy) 

ggsave(here("res/plots/accuracy_full.png"), plot = accuracy, 
       width = 7, height = 5)

```


#### Planned Analyses
Planned bonferroni contrasts are performed for the following comparisons.
* main effect of training - 1. stable v.s. variable training
* main effects of transfer - 1. novel v.s. partial, 2. novel v.s. complete, 3. partial v.s. complete
* interaction effects - 1. group x transfer (novel vs. partial) and 2. group x transfer (partial vs. complete)

*Only the main effect of novel vs. complete transfer returned significant. Difference between novel and part almost returns significant*

```{r planned comparisons accuracy, echo=FALSE}
# fit the data to an ANOVA model
accuracy_anova <- aov_ez('sub',
                         'mean_acc', 
                         all_transfer_data, 
                         between = 'train_type',
                         within = 'transfer')

print(accuracy_anova)

# get estimated marginal means
accuracy_emm <- emmeans(accuracy_anova, c("train_type", "transfer"))

print(accuracy_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_acc <- contrast(accuracy_emm, within_main, adjust = "bonferroni")

print(transfer_main_acc)


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_acc <- contrast(accuracy_emm, interactions, adjust = "bonferroni")

print(interactions_acc)

```

To remove mitigate any order effects, accuracy can be assessed using a between subjects design, by comparing performance on the first transfer condition across groups. This however, significantly reduces power.

```{r accuracy between subjects, echo=FALSE, warning=FALSE}

# specifying the order that I want my transfer conditions to appear
# all_btwn_transfer_data$transfer <- factor(
#   all_transfer_data$transfer,
#   levels = c("Novel", "Partial", "Complete")
# )

# specifying key variables
data <- all_btwn_transfer_data
iv <- all_btwn_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_btwn_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

# now plotting
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
acc_between_subs <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0.5, 1), breaks = seq(0.5, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(acc_between_subs) 

```

To determine whether the strength of a routine correlated with performance in transfer, we will also correlate transition entropy to bias scores for partial transfer accuracy, relative to performance on the:
1. novel condition where bias = partial/(partial + novel)
2. complete transfer where bias = partial/(partial + complete)

To do this, we will first check whether the data for transition entropy and the bias scores is skewed.

```{r bias and TE skewness, echo = FALSE, warning = FALSE}

bias_scores <- read.csv(here("res/transfer_bias_scores.csv"))

# histograms
ggplot(data = bias_scores, aes(x = bias_ovr_complete)) +
  geom_histogram(fill = 'pink') +
  theme_classic() +
  labs(x = "Bias Score: Partial/(Partial + Complete)", y = "Frequency") +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))

ggplot(data = bias_scores, aes(x = bias_ovr_novel)) +
  geom_histogram(fill = 'pink') +
  theme_classic() +
  labs(x = "Bias Score: Partial/(Partial + Novel)", y = "Frequency") +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))

ggplot(data = training_entropy, aes(x = mean_entropy)) +
  geom_histogram(fill = 'pink') +
  theme_classic() +
  labs(x = "Transition entropy", y = "Frequency") +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))

# Q-Q plots
qq_novel_bias <- ggplot(data = bias_scores, aes(sample = bias_ovr_novel)) + 
  geom_qq(colour = 'blue') +
  geom_qq_line(color = "grey")+
  labs(title = "Q-Q plot for bias scores partial/(partial + novel)",
        x = 'theoretical',
        y = 'sample') +
  # labs(title = 'Q-Q plots for transition entropy',
  #      x = 'theoretical',
  #      y = 'sample') +
  theme_classic() +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))


ggsave(here("res/plots/qq_novel_bias.png"), plot = qq_novel_bias, width = 7, height = 5)

```

Based off visual inspection of Q-Q plots, the data for transition entropy and bias are skewed. Hence, a log transformation will be performed on the data.

```{r transforming bias scores and TE, echo = FALSE, warnings = FALSE}

# combined the data into one data frame first
bias_scores <- inner_join(bias_scores, training_entropy, by = c('sub', 'train_type'))

bias_scores <- bias_scores %>% 
  mutate(log_bias_comp = log(bias_ovr_complete),
         log_bias_novel = log(bias_ovr_novel),
         log_entropy= log(mean_entropy))

```

Now, lets visualise the transformed data in Q-Q plots again.

```{r Q-Q plots post transformation, echo = FALSE, warnings = FALSE}

# Q-Q plots
qq_TE_transformed <- ggplot(data = bias_scores, aes(sample = log_entropy)) + 
  geom_qq(colour = 'blue') +
  geom_qq_line(color = "grey")+
  # labs(title = "Q-Q plot for bias scores partial/(partial + complete) post transformation",
  #       x = 'theoretical',
  #       y = 'sample') +
   labs(title = 'Q-Q plots for transition entropy post transformation',
        x = 'theoretical',
        y = 'sample') +
  theme_classic() +
  theme(
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)))

ggsave(here("res/plots/qq_TE_transformed.png"), plot = qq_TE_transformed, width = 7, height = 5)


```

Now we can plot the correlation between transition entropy and the two bias scores.
```{r TE and bias correlation, echo = FALSE, warning = FALSE}

# # correlating TE with bias scores over complete accuracy
# TExcomplete_bias <- ggplot(data = bias_scores, 
#                            aes(x = mean_entropy,
#                                y = bias_ovr_complete)) +
#   geom_point(colour = "orange") +
#   theme_classic()
# print(cor(bias_scores$bias_ovr_complete, bias_scores$mean_entropy)) # r = 0.01
# model <- lm(bias_scores$bias_ovr_complete ~ bias_scores$mean_entropy)
# summary(model)
# 
# # correlating TE with bias scores over novel accuracy
# TExnovel_bias <- ggplot(data = bias_scores, 
#                            aes(x = mean_entropy,
#                                y = bias_over_novel)) +
#   geom_point(colour = "orange") +
#   theme_classic()
# print(cor(bias_scores$bias_ovr_novel, bias_scores$mean_entropy)) # r = 0.12
# 
# print(TExcomplete_bias)


```



### Learning Onset
Learning onset quantifies how long it takes to learn the target locations by determining the trial at which there is evidence for knowledge of all four target locations in each task.  

Learning onset is calculated using a Bayesian algorithm (Maggi et al., 2024) which applies the beta distribution to model the amount of evidence for a particular behavioural strategy on a trial-by-trial basis. To do this, every trial is assessed for whether it contains evidence for an informed (non-guessed) selection of each door. 

Criteria for coding evidence of doors for learning onset are as follows:
* all door selections made before an error scored a 1
* all door selections made after an error are scored a 0
* any missing door selections are scored a 1, if there was evidence of knowledge for that door on the most recent trial it was selected. If else, assign it a value of NA.

E.g., for a door sequence of door selections ‘A-B-X-Y-C', doors A and B are assigned a value of 1, door C is assigned 0. Door D which is missing from the sequence of clicks is assigned 1, if it was correctly selected before an error on the last trial a click on Door D was recorded, and NA if else. 


```{r learning onset, echo = FALSE, warning=FALSE}

# specifying the order that I want my transfer conditions to appear
learn_onset_data$transfer <- factor(
  learn_onset_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

# specifying key variables
data <- learn_onset_data
iv <- learn_onset_data$transfer
x_axis_lab <- 'Transfer type'
dv <- learn_onset_data$k4_onset
y_axis_lab <- 'Learning Onset'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

# now plot
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
learning_onset <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub),
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 40), breaks = seq(0, 40, by = 10)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(learning_onset)

```

Note: 12 cases who never meet the criteria for learning onset are not included in the figure above. The number of subjects in each group who are considered 'non-learners' are outlined below.

```{r non-learners, echo=FALSE, warning=FALSE}

print(non_learners)

```

Again, we can look at the learning onset data in a between subjects manner.


```{r between learning onset, echo = FALSE, warning=FALSE}
data <- learn_onset_btwn_data
iv <- learn_onset_btwn_data$transfer
x_axis_lab <- 'Transfer type'
dv <- learn_onset_btwn_data$k4_onset
y_axis_lab <- 'Learning Onset'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")


jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
between_learning_onset <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 40), breaks = seq(0, 40, by = 10)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(between_learning_onset)

```

Note: 5 participants never met the criteria for having learned all 4 doors and are not included in the previous figure. Performance for these participants are as follows.

```{r between non learners, echo=FALSE, warning=FALSE}

print(btwn_non_learners)

```

#### Planned Analyses
Planned contrasts are performed for learning onset as they are for accuracy. *No comparisons return significant.*

```{r planned comparisons learn onset, echo=FALSE, warnings = FALSE}
# fit the data to an ANOVA model
learn_onset_anova <- aov_ez('sub',
                         'k4_onset', 
                         learn_onset_data, 
                         between = 'train_type',
                         within = 'transfer')

print(learn_onset_anova)

# get estimated marginal means
learn_onset_emm <- emmeans(learn_onset_anova, c("train_type", "transfer"))

print(learn_onset_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_learn_onset<- contrast(learn_onset_emm, within_main, adjust = "bonferroni")

print(transfer_main_learn_onset)


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_learn_onset <- contrast(learn_onset_emm, interactions, adjust = "bonferroni")

print(interactions_learn_onset)

```


### Number of locations learned

This measure tells us whether participants are following a strategy of using 1, 2, 3, or 4 target locations on the last trial of each transfer condition (i.e., by the end of that transfer condition).

```{r ndoors learned, echo = FALSE, warning=FALSE}

# specifying the order that I want my transfer conditions to appear
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

# specifying key variables
data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$n_learned
y_axis_lab <- 'N locations learned'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

# now plot
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
ndoors <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub),
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0,4), breaks = seq(0, 4, by = 1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(ndoors)

```

#### Planned Analyses
Planned contrasts are performed for n learned as they are for accuracy and learn onset. *No comparisons return significant.*

```{r planned comparisons n learned, echo=FALSE, warnings = FALSE}
# fit the data to an ANOVA model
ndoors_anova <- aov_ez('sub',
                         'n_learned', 
                         all_transfer_data, 
                         between = 'train_type',
                         within = 'transfer')

print(ndoors_anova)

# get estimated marginal means
ndoors_emm <- emmeans(ndoors_anova, c("train_type", "transfer"))

print(ndoors_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_ndoors<- contrast(ndoors_emm, within_main, adjust = "bonferroni")

print(transfer_main_ndoors)


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_ndoors <- contrast(ndoors_emm, interactions, adjust = "bonferroni")

print(interactions_ndoors)

```

### Setting Errors
Setting-error quantifies the extent to which participants apply previously learned target locations which are not relevant to the current task. Since the number of relevant doors differ between the transfer and novel conditions, setting-error for partial and complete transfer will be calculated differently to the novel task condition.  

For partial and complete transfer, setting-error is calculated as the proportion of total door selections which were previously relevant to Task A or B but have not been transferred to the current task-setting. 

For the novel task condition, setting-error will be calculated as the proportion of door selections from Task A and B. 

```{r setting errors, echo=FALSE, warning=FALSE}

# specifying the order I want transfer conditions to appear in
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_set_error
y_axis_lab <- 'Setting Error'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
setting_error <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 0.5), breaks = seq(0, 0.5, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(setting_error)

ggsave(here("res/plots/setting_error.png"), plot = setting_error, width = 7, height = 5)

```


#### Planned Analyses
We will perform a 2 (Group: stable vs variable) x 2 Transfer(partial vs. complete) contrast analysis, and a separate between groups comparison of setting error on the novel transfer condition.

*No significant differences from any of these contrasts.*

```{r planned analyses setting error, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
set_error_anova <- aov_ez('sub',
                         'mean_set_error', 
                         all_transfer_data, 
                         between = 'train_type',
                         within = 'transfer')

print(set_error_anova)

# get estimated marginal means
set_error_emm <- emmeans(set_error_anova, c("train_type", "transfer"))

print(set_error_emm)

# specify contrasts and run analyses for:
# interaction family (k = 1)
interaction <- c(0, 0, 1, -1, -1, 1)
interactions <- list("groupxpartialvs.complete" = interaction)
interaction_set_error <- contrast(set_error_emm, interactions, adjust = "bonferroni")

print(interaction_set_error)

## simple effects, (k = 1)
group_effect_novel <- c(1, -1, 0, 0, 0, 0)
group_simple_effects <- list(group_effect_novel)
group_effect_set_error <- contrast(set_error_emm, group_simple_effects, adjust = "bonferroni")

print(group_effect_set_error)


```

Again, we can look at Setting Errors using as between subjects design again.

```{r setting error between subjects, echo=FALSE, warning=FALSE}
data <- all_btwn_transfer_data
iv <- all_btwn_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_btwn_transfer_data$mean_set_error
y_axis_lab <- 'Setting Error'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
set_error_between_subs <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 0.5), breaks = seq(0, 0.5, by = 0.1))  +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(set_error_between_subs) # same order issue as above

```


## Individual Difference Measures

### Target location memory
```{r target location memory, echo=FALSE, warnings=FALSE}
data <- ind_diffs
iv <- ind_diffs$train_type
x_axis_lab <- 'Group'
dv <- ind_diffs$mean_locs_correct
y_axis_lab <- 'mean locations correct'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


target_mem <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 4, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(target_mem)


```

#### Exploratory analyses
We can compare the number of target locations remembered between groups to determine whether training or transfer interrupted memory of the locations.

```{r}
ttestBF(formula = mean_locs_correct ~ train_type, data = ind_diffs)

```


## Additional Analyses

### Where are the general errors?
To probe the source of general errors (e.g., whether stable training is causing people to forget the other task set), we can look at the where the general errors are. To do this, I am plotting of general errors which are one, two or 2+ doors away from the nearest target location from the other task set.

```{r gen error distances, echo=FALSE, warning=FALSE}

gen_error_dist <- read.csv(here("res/gen_error_summary.csv"))

gen_error_dist <- gen_error_dist %>% 
  pivot_longer(cols = c(one_door, two_door, two_plus_doors),
               names_to = "distance",
               values_to = "proportion_errors")

data <- gen_error_dist
iv <- gen_error_dist$distance
x_axis_lab <- 'n doors away'
dv <- gen_error_dist$proportion_errors
y_axis_lab <- 'proportion of total general errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 2, 4)]
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 

gen_error_dist <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 21, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'grey20', 
               linewidth = 0.5)+
  scale_y_continuous(limits = c(0, 0.5), breaks = seq(0, 0.5, by = 0.1))  +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_grid(~ train_type*switch) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(gen_error_dist)


```



### Task jumps over time 
We can also look at task jumps overtime.

```{r task jumps by epoch, echo=FALSE, warning=FALSE}

jumps_by_epoch <- ggplot(training_by_epoch, aes(x = epoch, y = group_task_jumps)) +
  geom_point(alpha = 0.7) +
  geom_line() +
  facet_wrap(~ train_type) +
  labs(x = "Epoch", y = "Task Jumps") +
  theme_classic() 

print(jumps_by_epoch)

```

### General Errors over time 
I am plotting general errors over time to check if scores are stable across training. A median split has been performed to separate participants into a high error group and a low error group.

```{r gen error by epoch, echo=FALSE, warning=FALSE}

med_split_data <- read.csv(here("res/med_split_gen_error.csv"))

gen_error_by_epoch <- ggplot(med_split_data, aes(x = epoch, y = gen_error, colour = error_group, fill = error_group)) +
  geom_point(size = 1.3) +
  geom_line(linewidth = 0.8) +
  labs(x = "Epoch", y = "General Error", 
       colour = 'Error Group', fill = 'Error Group') +
  scale_x_continuous(limits = c(1, 8), breaks = seq(1, 8, by = 1))+
  theme_classic() +
  facet_wrap(~train_type)

print(gen_error_by_epoch)

ggsave(here("res/plots/gen-error_by_epoch.png"), plot = gen_error_by_epoch, width = 7, height = 5)

```

### Transfer Accuracy by First Transfer Condition
To determine whether performance one one transfer condition affected performance on subsequent transfer conditions, we can plot the accuracy data based on the first transfer condition people received.

```{r accuracy by first transfer condition, echo = FALSE, warning=FALSE}

all_transfer_data$first_transfer <- factor(
  all_transfer_data$first_transfer,
  levels = c("novel first", "partial first", "complete first")
)
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
accuracy_by_first_trf <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0.4, 1), breaks = seq(0.4, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_grid(~first_transfer*train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(accuracy_by_first_trf)


```

#### Exploratory analyses
We can determine whether order affects performance on transfer by assessing for a three way interaction between first transfer condition, group, and transfer condition.

*Interaction is not significant*

```{r order interaction, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
order_anova <- aov_ez('sub',
                      'mean_acc', 
                      all_transfer_data, 
                      between = c("first_transfer", 'train_type'),
                      within = 'transfer')

print(order_anova)

```


### Transfer Accuracy by Task-set

We can also examine whether similarity in the two learned task-sets influences performance on each of the transfer conditions. It may be that when two task sets are more similar (i.e., when there is more overlap in two task-sets), participants are better able to perform partial transfer. The following plot provides an illustration of any differences between the four sets of Task A and B that were given to participants. However, more work would be needed to quantify how similar two task-sets are.

**There is no interaction between task-set configuration, transfer and group.**

```{r transfer by task-set, echo=FALSE, warning=FALSE}

all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
accuracy_by_taskset <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0.4, 1), breaks = seq(0.4, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_grid(~task_set*train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(accuracy_by_taskset)


```


```{r task-set interaction, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
task_set_anova <- aov_ez('sub',
                      'mean_acc', 
                      all_transfer_data, 
                      between = c("task_set", 'train_type'),
                      within = 'transfer')

print(task_set_anova)

```

