---
title: "res_summary_w/exclusion"
author: E.Chung
output: html_document
date: "2026-01-27"
---

# Document Summary
This document contains the same plots and analyses used to assess for performance in the doors experiment as performed in the res_summary.Rmd file in this folder. **Crucially**, all analyses in this document will be run with a subset of poor performers excluded from the data set. All of these participants come from the Stable training group and have a general error score > 0.2 on switch trials. 

Some exploratory analyses performed in the previous document are not included in this document for conciseness.

```{r setup, include=FALSE}
# load libraries 
library(here) # setting working directory to the project directory
library(tidyverse)
library(dplyr)

library(ggplot2) # libraries for plotting data
library(gridExtra)
library(wesanderson)
library(gghalves)

library(afex) # libraries for performing planned contrast analyses
library(emmeans)
library(BayesFactor)
afex_options(emmeans_model = "multivariate")

# load dataframes
training_data <- read.csv(here("res/training_jumps_gen-error.csv"))
training_entropy <- read.csv(here("res/training_entropy.csv"))
training_entropy_stay <- read.csv(here("res/training_STAY_entropy.csv"))

all_transfer_data <- read.csv(here("res/all_transfer_data.csv"))
non_learners <- read.csv(here("res/nonlearners.csv"))
learn_onset_data <- read.csv(here("res/post_exclusion_transfer_data.csv"))

task_memory_data <- read.csv(here("res/task_memory_summary.csv"))
ind_diffs <- read.csv(here("res/all_individual_differences.csv"))

```

## Training Stage

Three key measures are used to assess performance in the Training Stage:
- Task jumps 
- Transition entropy
- General Errors

**Are these participants the same as those classified as outliers i.e., 2.5 SDs from the mean in the res_summary.Rmd doc?**

```{r train data removal, echo=FALSE, warning=FALSE}

subs_to_remove <- training_data %>% 
  filter(mean_gen_error > 0.2) %>% 
  pull(sub) %>% 
  unique()

print(subs_to_remove)

training_data <- training_data %>% 
  filter(!sub %in% subs_to_remove)

```

### Task Jumps
Task jumps is used to measure the mixing of the two tasks during training.

```{r task jumps, echo=FALSE, warning=FALSE}

iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_task_jumps
y_axis_lab <- 'Task Jumps'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


task_jumps <- ggplot(data = training_data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 7.5, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(task_jumps)

```

#### Planned Analyses
We will perform a 2 (Group: stable vs. variable) x 2 (Trial Type: stay vs. switch) interaction contrast. Analysis with the full data set produced a significant interaction effect. Analyses with the current data set **also returned a significant interaction effect**. 

```{r planned comparisons task jumps, echo=FALSE}
# fit the data to an ANOVA model
task_jumps_anova <- aov_ez('sub',
                         'mean_task_jumps', 
                         training_data, 
                         between = 'train_type',
                         within = 'switch')

print(task_jumps_anova)

# get estimated marginal means
task_jumps_emm <- emmeans(task_jumps_anova, c("train_type", "switch"))

print(task_jumps_emm)

```

#### Follow Up Analyses
To investigate the source of interaction in task jumps, I will contrast task jumps between groups for each trial type separately and across trial types for each group separately. In the previous analysis, there was a significantly higher number of task jumps in the variable group compared to the stable group on stay trials. In addition, those in the stable group had a greater number of task jumps on switch trials compared to stay trials.

Analysis with this data set returns **three** significant contrasts.
- effect of group on *stay trials*
- effect of trial type in the *stable group*
- effect of trial type in the *variable group*. This last effect was not previously significant.

```{r task jumps follow up contrasts}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(task_jumps_emm, simple_effects, adjust = "bonferroni")

```
### General Errors

General errors is used to determine whether the training manipulation affected memory of tasks. 

```{r general errors, echo = FALSE, warning=FALSE}
data <- training_data
iv <- training_data$switch
x_axis_lab <- 'Trial type'
dv <- training_data$mean_gen_error
y_axis_lab <- 'General Errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

gen_errors <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, 0.2), breaks = seq(0, 0.2, by = 0.1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    facet_wrap(~train_type) +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(gen_errors)  

```

#### Planned analyses
We will assess for a 2 (Group: stable vs. variable) x 2 (Trial Type: switch vs. stay) interaction for general errors. In the previous analysis with the full data set, this test returned a significant result. This **interaction remains significant with this data set**.

```{r planned comparisons general_errors, echo=FALSE}
# fit the data to an ANOVA model
gen_error_anova <- aov_ez('sub',
                         'mean_gen_error', 
                         training_data, 
                         between = 'train_type',
                         within = 'switch')

print(gen_error_anova)

# get estimated marginal means
gen_error_emm <- emmeans(gen_error_anova, c("train_type", "switch"))

print(gen_error_emm)

```
To investigate the source of this interaction, I will now contrast general errors between groups for each trial type separately, and between trial types for each group separately. With the full data set, general errors were significantly higher **only in the stable group** on switch trials compared to stay trials. In this data set, general error were higher on switch trials compared to stay trials for **both** the stable and variable groups separately. No differences were found between groups on any trial type.

```{r gen error follow up contrasts}

# simple effect contrast to probe difference between groups for each trial type separately, 
# and difference in trial type of each group separately

simple_effects <- list('stay_btwn_group' = c(1, -1, 0, 0),
                       'switch_btwn_group' = c(0, 0, 1, -1), 
                       'stable_trial_type' = c(1, 0, -1, 0),
                       'variable_trial_type' = c(0, 1, 0, -1)
                       )

contrast(gen_error_emm, simple_effects, adjust = "bonferroni")

```

#### Are the general error rates stable across time?
To understand the source of general errors in the poor performers, we can compare general errors on switch and stay trials over time between people who are classified as poor performers, the remaining participants in the stable group, and those in the variable group.

```{r gen error over time, echo=FALSE, warning=FALSE, fig.show = 'hold', out.width = "50%"}

all_epoch_data<- read.csv(here("res/training_epochs.csv"))

subset_epoch_data <- all_epoch_data %>% 
  filter(sub %in% subs_to_remove) 
subset_epoch_data <- subset_epoch_data %>% 
  group_by(train_type, switch, epoch) %>% 
  summarise(mean_error = mean(mean_gen_error))
filtered_epoch_data <- all_epoch_data %>% 
  filter(!sub %in% subs_to_remove)
filtered_epoch_data <- filtered_epoch_data %>% 
  group_by(train_type, switch, epoch) %>% 
  summarise(mean_error = mean(mean_gen_error))


subset_gen_error_overtime <- ggplot(subset_epoch_data, aes(x = epoch, y = mean_error, colour = switch, fill = switch)) +
  geom_point(size = 1.5) +
  geom_line(linewidth = 0.8) +
  labs(x = "Epoch", y = "General Error", 
       colour = 'Trial Type', fill = 'Trial Type') +
  scale_x_continuous(limits = c(1, 8), breaks = seq(1, 8, by = 1))+
  theme_classic() +
  theme(legend.position = "none")

print(subset_gen_error_overtime)

gen_error_overtime <- ggplot(filtered_epoch_data, aes(x = epoch, y = mean_error, colour = switch, fill = switch)) +
  geom_point(size = 1.5) +
  geom_line(linewidth = 0.8) +
  labs(x = "Epoch", y = "General Error", 
       colour = 'Trial Type', fill = 'Trial Type') +
  scale_x_continuous(limits = c(1, 8), breaks = seq(1, 8, by = 1))+
  scale_y_continuous(limits = c(0, 0.4), breaks = seq(0, 0.4, by = 0.1))+
  theme_classic() +
  facet_wrap(~train_type)

print(gen_error_overtime)

# ggsave(here("res/plots/gen-error_by_epoch.png"), plot = gen_error_by_epoch, width = 7, height = 5)


```

#### Where are the general errors?
To probe the source of general errors (e.g., whether stable training is causing people to forget the other task set), we can look at the where the general errors are. To do this, I am plotting of general errors which are one, two or 2+ doors away from the nearest target location from the other task set.

```{r separating gen error dataframes, echo=FALSE, warning=FALSE}

# getting summary of error for poor performers and remaining participants

gen_error_events <- read.csv(here("res/exp_lt_gen-error_events.csv"))
gen_error_events$train_type <- as.factor(gen_error_events$train_type)
levels(gen_error_events$train_type) <- c("Stable", "Variable")
gen_error_events$switch <- as.factor(gen_error_events$switch)
levels(gen_error_events$switch) <- c("Stay", "Switch")

gen_error_events <- gen_error_events %>% 
  mutate(error_dist_ndoors = case_when(gen_error_dist == 1 ~ as.factor(1),
                                       gen_error_dist == 2 ~ as.factor(2),
                                       gen_error_dist > 2 ~ '2+')) %>% 
  select(sub, ses, t, context, door, door_nc, switch, train_type, gen_error_dist, error_dist_ndoors)


subset_error_evts <- gen_error_events %>% 
  filter(sub %in% subs_to_remove)
error_evts <- gen_error_events %>% 
  filter(!sub %in% subs_to_remove)

subset_error_summary <- subset_error_evts %>% 
  group_by(sub, train_type, switch) %>% 
  summarise(one_door = mean(error_dist_ndoors == 1),
            two_door = mean(error_dist_ndoors == 2),
            two_plus_doors = mean(error_dist_ndoors == '2+'))
subset_error_summary <- subset_error_summary %>% 
  pivot_longer(cols = c(one_door, two_door, two_plus_doors),
               names_to = "distance",
               values_to = "proportion_errors")

error_summary <- error_evts %>% 
  group_by(sub, train_type, switch) %>% 
  summarise(one_door = mean(error_dist_ndoors == 1),
            two_door = mean(error_dist_ndoors == 2),
            two_plus_doors = mean(error_dist_ndoors == '2+'))
error_summary <- error_summary %>% 
  pivot_longer(cols = c(one_door, two_door, two_plus_doors),
               names_to = "distance",
               values_to = "proportion_errors")

```


```{r gen error distances, echo=FALSE, warning=FALSE, fig.show='hold', out.width = "50%"}

x_axis_lab <- 'n doors away'
y_axis_lab <- 'proportion of total general errors'
these_cols <- wes_palette("AsteroidCity3")[c(1, 2, 4)]
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 

subset_gen_error_dist <- ggplot(data = subset_error_summary, 
                mapping = aes(x = distance, y = proportion_errors, colour = distance, fill = distance)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 21, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'grey20', 
               linewidth = 0.5)+
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.25))  +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~switch) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(subset_gen_error_dist)

gen_error_dist <- ggplot(data = error_summary, 
                mapping = aes(x = distance, y = proportion_errors, colour = distance, fill = distance)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 21, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'grey20', 
               linewidth = 0.5)+
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_grid(~ train_type*switch) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(gen_error_dist)


```




### Transition Entropy
Transition entropy assess how routine people are in their search paths.

```{r data removal transition entropy}

training_entropy <- training_entropy %>% 
  filter(!sub %in% subs_to_remove)

```

```{r transition entropy, echo = FALSE, warning=FALSE}
data <- training_entropy
iv <- training_entropy$train_type
x_axis_lab <- 'Group'
dv <- training_entropy$mean_entropy
y_axis_lab <- 'Transition Entropy'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]

entropy <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 40, by = 10)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(entropy)

```

#### Planned Analyses
A between groups comparison will be performed to determine any differences in transition entropy between groups. No difference was detected between groups on transition entropy with the full data set. Similarly, no significant difference was detected for this data set (although the p value is now closer to 0.05).

```{r planned comparisons transition entropy, echo=FALSE}
# fit the data to an ANOVA model
entropy_anova <- aov_ez('sub',
                         'mean_entropy', 
                         training_entropy, 
                         between = 'train_type')

print(entropy_anova)

```

#### Exploratory Analyses
It is interesting that there is no difference in transition entropy scores between groups, despite higher task jumps in the variable group compared to the stable group. Is this simply due to the variable group making more clicks and thereby, more 'jumps' on each trial? To assess this, we should check whether there are any difference in the avaerage number of clicks on each trial between groups. 

```{r nclicks}

nclicks <- read.csv(here("res/training_nclicks.csv"))
nclicks <- nclicks %>% 
  filter(!sub %in% subs_to_remove)
  
data <- nclicks
iv <- nclicks$train_type
x_axis_lab <- 'Group'
dv <- nclicks$nclicks
y_axis_lab <- 'n clicks'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


nclicks_btwn <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(nclicks_btwn)

ggsave(here("res/plots/nclicks_post-excl.png"), plot = nclicks_btwn, width = 7, height = 5)

```

## Transfer Test Stage

Three key measures are used to assess performance during the Transfer Test Stage of the experiment.
* Accuracy
* Learning Onset
* Setting Error

```{r transfer data removal}

all_transfer_data <- all_transfer_data %>% 
  filter(!sub %in% subs_to_remove)

learn_onset_data <- learn_onset_data %>% 
  filter(!sub  %in% subs_to_remove)

```

### Accuracy

Accuracy is a measure of performance in the transfer task. It is the proportion of door selections which are relevant to the current task, relative to the total number of door selections. Accuracy is averaged across trials for each participant. 

```{r accuracy, echo = FALSE, warning=FALSE}

# specifying the order that I want my transfer conditions to appear
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

# specifying key variables
data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_acc
y_axis_lab <- 'Accuracy'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

# plotting now
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
accuracy <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0.4, 1), breaks = seq(0.4, 1, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(accuracy) 

```

#### Planned Analyses
Planned bonferroni contrasts are performed for the following comparisons.
* main effect of training - 1. stable v.s. variable training
* main effects of transfer - 1. novel v.s. partial, 2. novel v.s. complete, 3. partial v.s. complete
* interaction effects - 1. group x transfer (novel vs. partial) and 2. group x transfer (partial vs. complete)

With the full data set, only the main effect of novel vs. complete transfer returned significant. This remains for the current data set.

```{r planned comparisons accuracy, echo=FALSE}
# fit the data to an ANOVA model
accuracy_anova <- aov_ez('sub',
                         'mean_acc', 
                         all_transfer_data, 
                         between = 'train_type',
                         within = 'transfer')

print(accuracy_anova)

# get estimated marginal means
accuracy_emm <- emmeans(accuracy_anova, c("train_type", "transfer"))

print(accuracy_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_acc <- contrast(accuracy_emm, within_main, adjust = "bonferroni")

print(transfer_main_acc)


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_acc <- contrast(accuracy_emm, interactions, adjust = "bonferroni")

print(interactions_acc)

```

### Learning Onset
Learning onset quantifies the number of trials it takes for all locations for a single task to be sufficiently learned.

```{r learning onset, echo = FALSE, warning=FALSE}

# specifying the order that I want my transfer conditions to appear
learn_onset_data$transfer <- factor(
  learn_onset_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

# specifying key variables
data <- learn_onset_data
iv <- learn_onset_data$transfer
x_axis_lab <- 'Transfer type'
dv <- learn_onset_data$k4_onset
y_axis_lab <- 'Learning Onset'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

# now plot
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
learning_onset <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub),
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 40), breaks = seq(0, 40, by = 10)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(learning_onset)

```

#### Planned Analyses
Planned contrasts are performed for learning onset as they are for accuracy. These analyses returned no significant effects with the full data set or the current data set.

```{r planned comparisons learn onset, echo=FALSE, warnings = FALSE}
# fit the data to an ANOVA model
learn_onset_anova <- aov_ez('sub',
                         'k4_onset', 
                         learn_onset_data, 
                         between = 'train_type',
                         within = 'transfer')

print(learn_onset_anova)

# get estimated marginal means
learn_onset_emm <- emmeans(learn_onset_anova, c("train_type", "transfer"))

print(learn_onset_emm)

# specify contrasts and run analyses for:
group_main <- c(1, -1, 1, -1, 1, -1)

## within family, (k = 3)
novel_vs_part <- c(1, 1, -1, -1, 0, 0) 
part_vs_comp <- c(0, 0, 1, 1, -1, -1) 
novel_vs_comp <- c(1, 1, 0, 0, -1, -1) 
within_main <- list("novelvs.part" = novel_vs_part,
                    "partvs.comp" = part_vs_comp,
                    "novelvs.comp" = novel_vs_comp)
transfer_main_learn_onset<- contrast(learn_onset_emm, within_main, adjust = "bonferroni")

print(transfer_main_learn_onset)


## interaction family, (k = 2)
novel_part_int <- group_main*novel_vs_part
part_comp_int <- group_main*part_vs_comp
interactions <- list("groupxnovelvs.part" = novel_part_int, 
                     "groupxpartvs.comp" = part_comp_int)
interactions_learn_onset <- contrast(learn_onset_emm, interactions, adjust = "bonferroni")

print(interactions_learn_onset)

```

### Setting Error

Setting error is a measure of how much people transfer door locations that were previously relevant, but no longer in the current training context.

```{r setting errors, echo=FALSE, warning=FALSE}

# specifying the order I want transfer conditions to appear in
all_transfer_data$transfer <- factor(
  all_transfer_data$transfer,
  levels = c("Novel", "Partial", "Complete")
)

data <- all_transfer_data
iv <- all_transfer_data$transfer
x_axis_lab <- 'Transfer type'
dv <- all_transfer_data$mean_set_error
y_axis_lab <- 'Setting Error'
these_cols <- c("#8da0cb", "#e78ac3", "#a6d854")

jitter_pos <- position_jitterdodge(jitter.width = 0.01) 
  
setting_error <- ggplot(data = data, 
                mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
  geom_point(aes(group = sub), 
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  geom_line(aes(group = sub), 
            alpha = 0.3, 
            colour = "grey",
            position = jitter_pos) +
  geom_boxplot(width = 0.2, 
               alpha = 0.8, 
               linewidth = 0.3, 
               colour = 'grey20', 
              outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
               colour = "grey20", fill = "grey20") +
  scale_y_continuous(limits = c(0, 0.5), breaks = seq(0, 0.5, by = 0.1)) +
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16)+
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 14),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 14),
    axis.title = element_text(face = "bold", color = "grey20", size = 16),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(setting_error)

```

#### Planned Analyses
We will perform a 2 (Group: stable vs variable) x 2 Transfer(partial vs. complete) contrast analysis, and a separate between groups comparison of setting error on the novel transfer condition. No significant differences from any of these contrasts with the full data set or the current data set.

```{r planned analyses setting error, echo=FALSE, warning=FALSE}

# fit the data to an ANOVA model
set_error_anova <- aov_ez('sub',
                         'mean_set_error', 
                         all_transfer_data, 
                         between = 'train_type',
                         within = 'transfer')

print(set_error_anova)

# get estimated marginal means
set_error_emm <- emmeans(set_error_anova, c("train_type", "transfer"))

print(set_error_emm)

# specify contrasts and run analyses for:
# interaction family (k = 1)
interaction <- c(0, 0, 1, -1, -1, 1)
interactions <- list("groupxpartialvs.complete" = interaction)
interaction_set_error <- contrast(set_error_emm, interactions, adjust = "bonferroni")

print(interaction_set_error)

## simple effects, (k = 1)
group_effect_novel <- c(1, -1, 0, 0, 0, 0)
group_simple_effects <- list(group_effect_novel)
group_effect_set_error <- contrast(set_error_emm, group_simple_effects, adjust = "bonferroni")

print(group_effect_set_error)

```

## Individual Difference Measures

```{r removing dubious performers, echo=FALSE, warning=FALSE}

task_memory_data <- task_memory_data %>% 
  filter(!sub %in% subs_to_remove)

```

### Target location memory
```{r task location memory, echo=FALSE, warnings=FALSE}
data <- task_memory_data
iv <- task_memory_data$train_type
x_axis_lab <- 'Group'
dv <- task_memory_data$mean_locs_correct
y_axis_lab <- 'mean locations correct'
these_cols <- wes_palette("AsteroidCity3")[c(1, 4)]


task_mem <- ggplot(data = data, 
                 mapping = aes(x = iv, y = dv, colour = iv, fill = iv)) +
    geom_half_violin(side = "r", scale = "width", 
                     width = 0.6,
                     alpha = 0.3, linewidth = 0.3, 
                     trim = FALSE) +
    geom_half_point(side = "l", alpha = 0.5, size = 1.5,
                    width = 0.6,
                    position = position_jitter(width = 0.05)) +
    geom_boxplot(width = 0.1, alpha = 0.9, linewidth = 0.3, colour = "grey20", 
                 outlier.shape = NA) +
    # scale_y_continuous(limits = c(0, max(dv)), breaks = seq(0, 4, by = 1)) +
    scale_fill_manual(values = these_cols) +
    scale_colour_manual(values = these_cols) +
    labs(x = x_axis_lab, y = y_axis_lab) + 
    stat_summary(fun = mean, geom = "point", shape = 23, size = 2, 
                colour = "grey20", fill = "grey20") +
    theme_classic(base_size = 16) +
    theme(
      legend.position = "none",
      strip.background = element_rect(fill = "#f0e6da", colour = NA),
      strip.text = element_text(face = "bold", size = 14),
      axis.line.x = element_line(color = "grey20", linewidth = 0.5),
      axis.line.y = element_line(color = "grey20", linewidth = 0.5),
      axis.ticks = element_line(color = "grey20", linewidth = 0.5),
      axis.text = element_text(color = "grey20", size = 14),
      axis.title = element_text(face = 'bold', color = "grey20", size = 16),
      axis.title.x = element_text(margin = margin(t = 10)),
      axis.title.y = element_text(margin = margin(r = 10)) 
    )
    
print(task_mem)


```

We can compare the number of target locations remembered between groups to determine whether training or transfer interrupted memory of the locations.

```{r ttest task location memory, echo = FALSE, warning = FALSE}
ttestBF(formula = mean_locs_correct ~ train_type, data = ind_diffs)

```


#### Task memory by transfer
Now, we can also compare the look at whether the proportion of doors remembered each learned task, in terms of whether it was transferred to the complete condition, partial condition, both, or not transferred at all.

```{r task memory wrt. transfer tasks, echo = FALSE, warning = FALSE}

# pivoting the data into long form
task_memory_by_trf <- task_memory_data %>% 
  pivot_longer(cols = c(comp_and_part, complete_only, partial_only, never_transferred),
               names_to = 'transferred_to',
               values_to = 'proportion_correct') %>% 
  select(sub, train_type, mean_locs_correct, all_complete, transferred_to, proportion_correct)

```

```{r plot task memory wrt. transfer tasks, echo=FALSE, warning=FALSE}

task_memory_by_trf$transferred_to <- factor(task_memory_by_trf$transferred_to,  # keeps the order of the conditions
                                            levels = unique(task_memory_by_trf$transferred_to))

# renaming conditions
levels(task_memory_by_trf$transferred_to) <- c("Both", "Complete Only", "Partial Only", "Never transferred")

# now plot
x_axis_lab <- 'learned doors by transfer condition'
y_axis_lab <- 'proportion correct'
these_cols <- wes_palette("AsteroidCity3")[c(1, 2, 3, 4)]
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 

plot_memory_by_trf <- ggplot(data = task_memory_by_trf, 
                mapping = aes(x = transferred_to, y = proportion_correct, colour = transferred_to, fill = transferred_to)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 21, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'grey20', 
               linewidth = 0.5)+
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~ train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(plot_memory_by_trf)

ggsave(here("res/plots/task_memory_by_trf_excl.png"), plot = plot_memory_by_trf, width = 7, height = 5)

```


```{r memory by group x transfered doors, echo=FALSE, warning=FALSE}

memory_means <- task_memory_by_trf %>% 
  group_by(train_type, transferred_to) %>% 
  summarise(mean(proportion_correct))
print(memory_means)

memory_by_trf_anova <- aov_ez('sub',
                         'proportion_correct', 
                         task_memory_by_trf, 
                         between = 'train_type',
                         within = 'transferred_to')

print(memory_by_trf_anova)

```

We can also split this comparison by whether people received complete before partial, or complete after partial, and when complete transfer came up in the transfer stage.

```{r getting transfer order by complete before or after partial, echo=FALSE, warning=FALSE}

# first, we should get the order that participants performed complete transfer, relative to partial
# and the position of complete transfer
order_data <- all_transfer_data %>% 
  select(sub, train_type, order_id) %>% 
  mutate(comp_vs_part_order = case_when(order_id %in% c(2, 3, 4) ~ "Complete before Partial",
                                        order_id %in% c(1, 5, 6)    ~ "Complete after Partial"),
         complete_pos = case_when(order_id %in% c(3, 4) ~ "1st",
                                  order_id %in% c(2, 5) ~ "2nd",
                                  order_id %in% c(1, 6) ~ "3rd")
         ) %>% 
  unique()

task_memory_by_trf <- inner_join(task_memory_by_trf, order_data, by = c('sub', 'train_type'))

```

```{r plot task memory by complete position relative to partial, echo=FALSE, warning=FALSE}

# reordering variables
task_memory_by_trf$comp_vs_part_order <-
  factor(
    task_memory_by_trf$comp_vs_part_order,
    levels = c("Complete before Partial", "Complete after Partial")
  )

# now plot
x_axis_lab <- 'learned doors by transfer condition'
y_axis_lab <- 'proportion correct'
these_cols <- wes_palette("AsteroidCity3")[c(1, 2, 3, 4)]
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 

plot_transfer_order <- ggplot(data = task_memory_by_trf, 
                mapping = aes(x = transferred_to, y = proportion_correct, colour = transferred_to, fill = transferred_to)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 21, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'grey20', 
               linewidth = 0.5)+
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~ comp_vs_part_order) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(plot_transfer_order)

ggsave(here("res/plots/task_memory_by_trf_order_excl.png"), plot = plot_transfer_order, width = 7, height = 5)

```

```{r memory by order x transfer, echo=FALSE, warning=FALSE}

memory_means <- task_memory_by_trf %>% 
  group_by(comp_vs_part_order, transferred_to) %>% 
  summarise(mean(proportion_correct))
print(memory_means)

memory_orderxtrf_anova <- aov_ez('sub',
                         'proportion_correct', 
                         task_memory_by_trf, 
                         between = 'comp_vs_part_order',
                         within = 'transferred_to')

print(memory_orderxtrf_anova)

```

#### Is there a recency effect of complete training on memory of the complete task set?
There are some participants who fail to remember the locations of the task transferred to the complete condition. We want to know whether this is due to a recency effect of performing complete transfer 1st, 2nd or 3rd during the transfer test phase. If there is a recency effect, we should see poorer memory of the complete task in participants who performed complete transfer first and the best memory in those who performed complete transfer 3rd.

```{r getting complete memory data, echo=FALSE, warning=FALSE}

complete_memory <- task_memory_by_trf %>% 
  select(-transferred_to, -proportion_correct) %>% 
  group_by(sub, train_type, all_complete, order_id, comp_vs_part_order, complete_pos) %>% 
  unique()

```

```{r complete recency effect, echo=FALSE, warning=FALSE}

complete_memory$complete_pos <- factor(complete_memory$complete_pos,  # keeps the order of the conditions
                                            levels = c('1st', '2nd', '3rd'))

# now plot
x_axis_lab <- 'complete transfer position'
y_axis_lab <- 'n correct'
these_cols <- wes_palette("AsteroidCity3")[c(1, 2, 4)]
jitter_pos <- position_jitterdodge(jitter.width = 0.01) 

complete_recency <- ggplot(data = complete_memory, 
                mapping = aes(x = complete_pos, y = all_complete, colour = complete_pos, fill = complete_pos)) +
  geom_point(aes(group = sub),
             alpha = 0.3, 
             size = 1.5,
             position = jitter_pos) +
  stat_summary(fun = mean, geom = "point", shape = 21, size = 2, 
               colour = "grey20", fill = "grey20") +
  stat_summary(fun = mean, geom = "line", 
               aes(group = 1), 
               colour = 'grey20', 
               linewidth = 0.5)+
  labs(x = x_axis_lab, y = y_axis_lab) +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = these_cols) +
  scale_colour_manual(values = these_cols) +
  facet_wrap(~ train_type) +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill = "#f0e6da", colour = "NA"),
    strip.text = element_text(face = "bold", size = 9),
    axis.line.x = element_line(color = "grey20", linewidth = 0.5),
    axis.line.y = element_line(color = "grey20", linewidth = 0.5),
    axis.ticks = element_line(color = "grey20", linewidth = 0.5),
    axis.text = element_text(color = "grey20", size = 9),
    axis.title = element_text(face = "bold", color = "grey20", size = 10),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_text(margin = margin(r = 10)) 
  )

print(complete_recency)

ggsave(here("res/plots/task_memory_recency_excl.png"), plot = complete_recency, width = 7, height = 5)



```
```{r complete recency anova, echo=FALSE, warning=FALSE}

memory_means <- complete_memory %>% 
  group_by(train_type, complete_pos) %>% 
  summarise(mean(all_complete))
print(memory_means)

complete_recency_anova <- aov_ez('sub',
                         'all_complete', 
                         complete_memory, 
                         between = c('complete_pos', 'train_type'))

print(complete_recency_anova)

```
